---
title: "Data_EDA"
author: "jian (AKA Frank) liu"
date: "`r Sys.Date()`"
output: html_document
---

# Protocol

- Load data from sqlite   
- Set constants. e.g. colours and keys  
- Set target  
    Key outcomes:   
    - Initial soil water content[Initial soil water]      
    - A set of DUL[DUL AND LL]  
    - A set of LL[DUL AND LL]  
- Calculation and summarising  
- Joining[Combine Soil Paras]  
- Set up directory structure[Set directory structure]  
- Invoke **Edit**  [Invoke Apsimx]  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 10, fig.height = 7, dpi = 300)
#Constants
outlier.colour = "#ff0000"
source("R/packages.R")
source("R/functions.R")
con <- dbConnect(SQLite(), "../03processed-data/Richard.sqlite3")
dbListTables(con)
SowingDates <- dbReadTable(con, "SowingDates") %>% 
  as.data.table()

```


```{r OverallAD, fig.cap='A boxplot shows the range of SWC in AshleyDene over 2 years.'}
water <- dbReadTable(con, "SoilWater", check.names = FALSE) %>% 
  as.data.table()

water[, ':='(Clock.Today = as.Date(Clock.Today))]
# [, SowingDate := factor(SowingDate, levels(SowingDate)[c(1,3:10, 2)])]
# Isolate SD 1 in AshleyDene
dbDisconnect(con)
# set key and make it order by dates and sowing date
setkey(water, Experiment, SowingDate, Clock.Today)
# water[, SWC:= NULL]
id_vars <- key(water)
value_vars <- grep("SW\\(\\d.+", colnames(water), value = TRUE)

```


# Initial soil water 

```{r}
SD <- SowingDates[, (c("AD", "I12")) := lapply(.SD, as.Date), .SDcols = c("AD", "I12")] %>% 
  melt(id.vars = "SD", 
       variable.name = "Experiment", value.name = "Clock.Today",
       variable.factor = FALSE) 
SD[, Experiment := ifelse(Experiment == "AD", "AshleyDene",  "Iversen12")]

SW_mean <- water[, lapply(.SD, mean, na.rm = TRUE), by = id_vars, .SDcols = value_vars]
SW_initials <- SW_mean[SD, on = c("Experiment", "SowingDate == SD", "Clock.Today"), roll = "nearest"]
SW_initials <- melt(SW_initials, 
                    id.vars = id_vars, variable.factor = FALSE,
                    variable.name = "Depth", value.name = "SW"
                    )[, ':='(SW = round(SW / 100, digits = 3))
                      ]

kable(SW_initials, caption = "Initial soil water content in each layer in 10 sowing dates")%>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
# Output the SW for different SDs
sites <- unique(SW_initials$Experiment)

```


# DUL AND LL

```{r}
# [SowingDate %in% paste0("SD", 1:5)]
DUL_LL <- water[, lapply(.SD, mean, na.rm = TRUE), 
                by = id_vars, .SDcols = value_vars # average 4 reps
                  ][, unlist(lapply(.SD, max_min), recursive = FALSE), 
                    by = .(Experiment, SowingDate), .SDcols = value_vars]

melted_DUL_LL <- melt(DUL_LL, 
                      id.var = c("Experiment","SowingDate"), 
                      variable.factor = FALSE) 
DUL_LL_SDs <- melted_DUL_LL[, (c("Depth", "variable")) := tstrsplit(variable, "\\.")] %>% 
  dcast(Experiment +  SowingDate + Depth ~ variable)

DUL_LL_SDsVWC <- DUL_LL_SDs[, ':='(DUL = round(DUL/100, digits = 3),
                                   LL = round(LL/100, digits = 3))
                            ][, PAWC := DUL - LL]
```


# Combine Soil Paras

```{r}
SW_DUL_LL <- SW_initials[DUL_LL_SDsVWC, on = c("Experiment", "SowingDate", "Depth")][Depth != "SW(2)"]

# Check if anything unusual 
SW_DUL_LL[DUL<SW]
SW_DUL_LL[LL>SW]

# Order the layers
SW_DUL_LL[, ':='(Depth = as.integer(gsub("\\D", "", Depth)),
                 SowingDate = fct_relevel(as.factor(SowingDate), paste0("SD", 1:10)))]
# order the order - CRITICAL 
setkey(SW_DUL_LL, Experiment, SowingDate, Depth)
kable(SW_DUL_LL, caption = "Initial soil parameters for 22 layers in 10 different sowing dates.")%>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")

# save the processed table for 
```
# Explore the python system call 

```{r}
library(reticulate)
```
```{python}
import sqlite3
import re
import datetime
import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
import os
import math
```

_Test_
```{python test}
con = sqlite3.connect('../03processed-data/Richard.sqlite3')
mycur = con.cursor() 
mycur.execute("SELECT name FROM sqlite_master WHERE type='table' ORDER BY name;")
(mycur.fetchall())
```

Check the configuration data

```{python}
print(r.SW_DUL_LL)
SDs = ['SD' + str(SD) for SD in range(1, 11)]
SDs
sites = ['AshleyDene', 'Iversen12']
sites
```
```{python}

for site in sites: 
    for i in SDs:
        r.SW_DUL_LL.loc[(r.SW_DUL_LL['Experiment'] == site) 
                       & (r.SW_DUL_LL.SowingDate == i),:].drop_duplicates().to_csv('../03processed-data/Config' + site + i + '.csv',index = False)
```


```{python}
print(r.SW_DUL_LL['Experiment'].to_series())
```

```{r}
## The Sowing date level configuration 

weather = ".Simulations.LnP.Expt.Weather.FileName = "
SD = ".Simulations.LnP.Expt.Field.ManagerFolder.SlurpSowingRule.SowingDate = "
CoverData = ".Simulations.LnP.Expt.Field.ManagerFolder.SetCropVariables.CoverFile = "
Height = ".Simulations.LnP.Expt.Field.ManagerFolder.SetCropVariables.MaximumHeight = "
initialSW = ".Simulations.LnP.LandPBase.Field.Soil.InitialConditions.SW = "

DUL <- ".Simulations.LnP.LandPBase.Field.Soil.Physical.DUL = "
AirDry <- ".Simulations.LnP.LandPBase.Field.Soil.Physical.AirDry = "
LL15 <- ".Simulations.LnP.LandPBase.Field.Soil.Physical.LL15 = "
SAT <- ".Simulations.LnP.LandPBase.Field.Soil.Physical.SAT = "

LL <- ".Simulations.LnP.Factors.Permutation.SKL.InitialKL.SlurpSoil.LL = "

## The kl parameter level configuration 
KL <- ".Simulations.LnP.LandPBase.Field.Soil.Physical.SlurpSoil.KL = "

```

```{r}
t1 <- Sys.time()
#path to apsimx 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_file <- "C:/Data/Master/01raw-data/ApsimxFiles/20200517BaseSlurp.apsimx"
apsimx_sims_temp <- "C:/Data/Master/03processed-data/apsimxFiles/temp.apsimx"
apsimx_sims_dir <- "C:/Data/Master/03processed-data/apsimxFiles/"
apsimx_config <- "C:/Data/Master/03processed-data/configSoilWat"
sites <- unique(SW_DUL_LL$Experiment)
SDs <- paste0("SD", 1:10)
# Vectorise the values 
for(j in sites){
  for(i in SDs){
    # Site specfied changes 
    met <- paste0(weather, )
    
    # Filter the right values 
    SDsw <- SW_DUL_LL[SowingDate == i & Experiment == j]$SW
    SDDUL <- SW_DUL_LL[SowingDate == i & Experiment == j]$DUL
    SDLL <- SW_DUL_LL[SowingDate == i & Experiment == j]$LL
    
    apsimx_sw <- paste0(initialSW,
                        paste(SDsw,collapse = ","))
    apsimx_DUL <- paste0(DUL,
                         paste(SDDUL,collapse = ","))
    apsimx_LL <- paste0(LL,
                        paste(SDLL,collapse = ","))
    apsimx_LL15 <- paste0(LL15,
                          paste(SDLL,collapse = ","))
    apsimx_SAT <- paste0(SAT,
                         paste(SDDUL,collapse = ","))
    # Open a text file
    f <- file(paste0(apsimx_config, j, i, ".txt"), "w")
    # Write values into the file 
    cat(apsimx_sw,
        apsimx_DUL,
        apsimx_LL,
        apsimx_LL15,
        apsimx_SAT,"\r",
        sep = "\r", 
        file = f, 
        append = TRUE)
    # Close the file and clean it from memory 
    close(f)
    rm(f)
    gc()
  }

}

t2 <- Sys.time()
t2 - t1
```

# Set directory structure

```{r}
t1 <- Sys.time()
#path to apsimx 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_file <- "C:/Data/Master/01raw-data/ApsimxFiles/20200520Demo.apsimx"
apsimx_sims_temp <- "C:/Data/Master/03processed-data/apsimxFiles/temp.apsimx"
apsimx_sims_dir <- "C:/Data/Master/03processed-data/apsimxFiles/"
apsimx_config <- "C:/Data/Master/03processed-data/configSoilWat"

# Node Path - copied from ApsimX UI

initialSW <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.InitialConditions.SW = "
DUL <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.DUL = "
LL <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.LucerneSoil.LL = "
LL15 <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.LL15 = "
# PAWC <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.PAWC = "
SAT <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.SAT = "
# Keys
sites <- unique(SW_DUL_LL$Experiment)
SDs <- paste0("SD", 1:10)

# Vectorise the values 
for(j in sites){
  for(i in SDs){
    # Filter the right values 
    SDsw <- SW_DUL_LL[SowingDate == i & Experiment == j]$SW
    SDDUL <- SW_DUL_LL[SowingDate == i & Experiment == j]$DUL
    SDLL <- SW_DUL_LL[SowingDate == i & Experiment == j]$LL
    apsimx_sw <- paste0(initialSW,
                        paste(SDsw,collapse = ","))
    apsimx_DUL <- paste0(DUL,
                         paste(SDDUL,collapse = ","))
    apsimx_LL <- paste0(LL,
                        paste(SDLL,collapse = ","))
    apsimx_LL15 <- paste0(LL15,
                          paste(SDLL,collapse = ","))
    apsimx_SAT <- paste0(SAT,
                         paste(SDDUL,collapse = ","))
    # Open a text file
    f <- file(paste0(apsimx_config, j, i, ".txt"), "w")
    # Write values into the file 
    cat(apsimx_sw,
        apsimx_DUL,
        apsimx_LL,
        apsimx_LL15,
        apsimx_SAT,"\r",
        sep = "\r", 
        file = f, 
        append = TRUE)
    # Close the file and clean it from memory 
    close(f)
    rm(f)
    gc()
  }

}

t2 <- Sys.time()
t2 - t1
```

# Invoke Apsimx

```{r}
t1 <- Sys.time()
for(j in sites){
   for(i in SDs){
     # Edit the base apsimx file and save it to a new name
     ## modify the apsimx file 
     system(paste(apsimx, apsimx_file, apsimx_flag, paste0(apsimx_config, j, i,".txt")))
     ## rename the modified one
     system(paste("cp", apsimx_file, paste0(apsimx_sims_dir, "Modified", j, i, ".apsimx")))
     ## delete the temp apsimx 
     # system(paste("rm", paste0(apsimx_sims_dir, "temp*")))
   }
  }
t2 <- Sys.time()
t2 - t1
```

```{r}
# system(apsimx)
t1 <- Sys.time()
# system(paste(apsimx, paste0(apsimx_sims_dir,"*.apsimx"), "/NumberOfProcessors:8"))
t2 <- Sys.time()
t2 - t1
```

It only takes 6 seconds for the apsimx ui to run 10 simulations. 