---
title: "kl estimation "
author: "jian (AKA Frank) liu"
date: "`r Sys.Date()`"
output: html_document
---

# Protocol

- Input data ready: met, cover and slurp `.apsimx`  
- Parameter ready: 
|Parameters|Units |Parameter levels tested |Description|
|:----|:----|:----|:----|
|RFV| mm/day| 10, 15, 20, 25, 30 and 35 |Maximum rate of root extension at 25 °C|
| $kl_{0}$|/day| 0.01, 0.03, 0.05, 0.07,0.09 and 0.11|Maximum kl value at surface layer(s)|
|$\lambda_{kl}$| dimensionless | −0.0005, −0.001,−0.002, −0.003,−0.005 and −0.01 | Exponential decay of kl0 with soil depth|  

- Set constant of key and values 

- Invoke **Edit**  [Invoke Apsimx]  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 10, fig.height = 7, dpi = 300)
#Constants
outlier.colour = "#ff0000"
source("R/packages.R")
source("R/functions.R")
con <- dbConnect(SQLite(), "../03processed-data/Richard.sqlite3")
dbListTables(con)
SowingDates <- dbReadTable(con, "SowingDates") %>% 
  as.data.table()

```


```{r subset}
biomass <- dbReadTable(con, "biomass", check.names = FALSE) %>% 
  as.data.table()
biomass[, ':='(Clock.Today = as.Date(Clock.Today))]
dbDisconnect(con)
# set key and make it order by dates and sowing date
setkey(biomass, Experiment, SowingDate, Clock.Today)
id_vars <- key(biomass)

LAI <- biomass[, .(LAImod), by = key(biomass)]
```


# Overview of the LAI
P88 in the thesis, 
LAI was calculated from $Specfic Leaf Area(SLA) \times TotalFW_{HarvestArea} \div 2000 $ 
```{r glimpse}


```




```{r graphLAI, fig.height=10}
LAI[, SowingDate := fct_relevel(as.factor(SowingDate), paste0("SD", 1:10))] %>% 
  ggplot(aes(Clock.Today, LAImod, color = SowingDate)) +
  geom_point() +
  geom_hline(yintercept = 1, colour = "#ff0000") +
  facet_grid(SowingDate~ Experiment) +
  theme_water()

LAI_summaried <- LAI[, LAImod := ifelse(LAImod == 0, NA, LAImod) # Some values are 0 which should be NAs
                     ][, list(mean = mean(LAImod, na.rm = TRUE)), by = id_vars
                       ][!is.na(mean)]

LAI_summaried %>% 
  ggplot(aes(Clock.Today, mean, color = SowingDate)) +
  geom_point() +
  geom_hline(yintercept = 1, colour = "#ff0000") +
  facet_grid(SowingDate~ Experiment) +
  theme_water()
# Output the SW for different SDs


```



# Slurp simulations setup in the .2_Data_EDA_Part2

# Slurp results analysis 

```{r}
con_eda <- dbConnect(SQLite(), "../03processed-data/apsimxFiles/ModifiedSKL_0.01AshleyDeneSD2.db")
dbListTables(con_eda)
report <- dbReadTable(conn = con_eda, "Report",  check.names = FALSE)%>% 
  as.data.table()
dbDisconnect(conn = con_eda)
```
## Subset the preds

```{r}
pred_swc_SD2 <- report[,.(Date = as.Date(Date), SimulationID,KLR, RFV, SKL, k, LAI, PSWC)][order(SimulationID)]
```

## Browse the preds


```{r, fig.height=10,fig.width=10}
pred_swc_SD2 %>% 
  ggplot(aes(Date, PSWC)) +
  geom_point() +
  facet_wrap(~ SimulationID)

```

## Subset the obs 

```{r}
con <- dbConnect(SQLite(), "../03processed-data/Richard.sqlite3")
water <- dbReadTable(con, "SoilWater", check.names = FALSE) %>% 
  as.data.table()
water[, ':='(Clock.Today = as.Date(Clock.Today))]
obs <- water[, lapply(.SD, mean, na.rm = TRUE), by = id_vars, .SDcols = "SWC" # average 4 reps
             ]
obs_SD2 <- water[, lapply(.SD, mean, na.rm = TRUE), by = id_vars, .SDcols = "SWC" # average 4 reps
      ][SowingDate == "SD2" & Experiment == "AshleyDene"]
```

## Join the pred and obs

```{r}
# Join and drop NAs of no obs
pred_obs <- pred_swc_SD2[obs_SD2, on = c(  "Date" = "Clock.Today" )][order(SimulationID)]
 # obs_SD2[pred_swc_SD2, on = c(  "Clock.Today" = "Date"), by = "SimulationID"]
# pred_obs[complete.cases(pred_obs)]
NSE(pred_obs$PSWC, pred_obs$SWC)
```

## Stats

```{r}
TEST <- pred_obs[SimulationID == 1]
m <- gof(sim = TEST$PSWC, obs = TEST$SWC) 
m[4] # RMSE
m[5] # Normalised RMSE
m[9] # NSE Nash-Sutcliffe Efficiency ( -Inf <= NSE <= 1 )
m[16] # Pearson Correlation coefficient ( -1 <= r <= 1 )
m[17] # Coefficient of Determination ( 0 <= R2 <= 1 ). 
      # Gives the proportion of the variance of one variable that is predictable from the other variable


setkey(pred_obs, "Experiment", "SimulationID", "SowingDate", "KLR","RFV","SKL")
# Nested the data.table by keys
nested <- pred_obs[, list(data = list(.SD)), by = key(pred_obs)][]
nested[, data := lapply(data, function(x){
  # Calculate the stats via goodness of fit
  m <- hydroGOF::gof(x$PSWC, x$SWC)
  # Convert the matrix into a data.table with colnames 
  m <- m %>% 
    as.data.table(keep.rownames = T) %>% 
    transpose(make.names = 'rn')
})]

# Unnest the data.table 
stats <- nested[, unlist(data, recursive = FALSE), by = key(pred_obs)]
stats
```

## visul check 



```{r}

pred_obs_withNAs <- obs_SD2[ pred_swc_SD2, on = c("Clock.Today" = "Date") ][order(SimulationID)]

pred_obs_withNAs %>% 
  ggplot(aes(Clock.Today, PSWC)) +
  geom_point(color = "grey") +
  geom_point(aes(y = SWC), color = "red") +
  facet_wrap(~ SimulationID)
  
```

# Try to process the whole 220 dbs

`for` loop to process one by one to avoid large memory usage? 

what are the necessary bits in the `for`

1. read db  
2. subset observation  
3. join the obs and preds   
4. nested the data.table   
5. calcualting inside the nested   
6. unnest  
7. store into the list  

## Test

```{r}
dbs <- list.files(path = "../03processed-data/apsimxFiles/", pattern = ".db$", full.names = TRUE)
i = dbs[10]
  con <- dbConnect(RSQLite::SQLite(), i)
  df <- dbReadTable(con, "Report", check.names = FALSE)
  dbDisconnect(con)
  dt <- as.data.table(df)
  site_sd <- gsub(".+ModifiedSKL_0\\.\\d{2}|\\.db","",i)
  site_sd <- gsub("(.+)(SD\\d{1,2})", "\\1_\\2", site_sd)
  site <- unlist(strsplit(site_sd, split = "_"))[1]
  sd <- unlist(strsplit(site_sd, split = "_"))[2]
  obs_sd <- obs[Experiment == site & SowingDate == sd]
dt
sd
site
```
# The workflow has been integrated into drake_plan

```
t1 <- Sys.time()
dbs <- list.files(path = "../03processed-data/apsimxFiles/", pattern = ".db$", full.names = TRUE)
# A list to store all the stats results 
l_stats <- vector("list", length = length(dbs))
names(l_stats) <- dbs
no <- 1L
for (i in dbs) {
  # 1 read db 
  con <- dbConnect(RSQLite::SQLite(), i)
  df <- dbReadTable(con, "Report", check.names = FALSE)
  dbDisconnect(con)
  dt <- as.data.table(df)
  # 2 subset 
  ## 2.1 Site and sowing date infor to subset the observation dt
  cat("Processing", i, no,"of", length(dbs), ".\r\n")
  no = no + 1L
  site_sd <- gsub(".+ModifiedSKL_0\\.\\d{1,2}|\\.db","",i)
  site_sd <- gsub("(.+)(SD\\d{1,2})", "\\1_\\2", site_sd)
  site <- unlist(strsplit(site_sd, split = "_"))[1]
  sd <- unlist(strsplit(site_sd, split = "_"))[2]
  obs_sd <- obs[Experiment == site & SowingDate == sd]
  
  ## 2.2 Subset necessary cols in prediction 
  pred_swc <- dt[,.(Date = as.Date(Date), SimulationID,KLR, RFV, SKL, k, LAI, PSWC)][order(SimulationID)]

  # 3 Join 
  pred_obs <- pred_swc[obs_sd, on = c("Date" = "Clock.Today" )][order(SimulationID)]
  
  # 4 nested the data.table   
  setkey(pred_obs, "Experiment", "SimulationID", "SowingDate", "KLR","RFV","SKL")
  nested <- pred_obs[, list(data = list(.SD)), by = key(pred_obs)]
  
  # 5 calcualting inside the nested   
  nested[, data := lapply(data, function(x){
    # Calculate the stats via goodness of fit
    m <- hydroGOF::gof(x$PSWC, x$SWC)
    # Convert the matrix into a data.table with colnames 
    m <- m %>% 
      as.data.table(keep.rownames = T) %>% 
      transpose(make.names = 'rn')
    })]
  # 6 Unnest the data.table 
  stats <- nested[, unlist(data, recursive = FALSE), by = key(pred_obs)]
  
  # 7 store into the list
  l_stats[[i]] <- stats


}
t2 <- Sys.time()
t2-t1
# 
# l_dbs <- lapply(dbs, function(x) {
#   con <- dbConnect(RSQLite::SQLite(), x)
#   df <- dbReadTable(con, "Report", check.names = FALSE)
#   dt <- as.data.table(df)
#   })
```


```
rbindlist(l_stats)
```
 
201 TO 220 has nothing? 
because the regex was wrong and subset ob failed. 

```{r}
l_stats[220]
```

# EDA on loadding stats from cache FOR 1 SKL

```{r}
DT_stats <- drake::readd(DT_stats)
# Check if any NAs
DT_stats[, lapply(.SD, function(x) sum(is.na(x)))]
# Check if any 0s - probably not very useful 
# DT_stats[, lapply(.SD, function(x) sum(which(x == 0)))]
```

# NSE needs to be close to 1 

NSE is acceptable if the value is above 

```{r}
# Nest it into different treatment 
setkey(DT_stats, "Experiment","SimulationID", "SowingDate", "KLR","RFV","SKL")
stats_nested = DT_stats[,.(stats), by = key(DT_stats)]
test = stats_nested[, unlist(stats, recursive = FALSE), by = key(stats_nested)]

# Best NSE for different treatment 
test = test[, list(stats = list(.SD)), 
            by = .(Experiment, SowingDate)
            ]
best_NSE= test$stats[[1]][order(NSE, R2, RMSE, decreasing = TRUE)][, .SD[.I[1]]]


# best_NSE = test$stats[[1]][order(NSE, decreasing = TRUE)][, .SD[.I[1]]]
```

# Check the best fit NSE for a single simulation 

```{r fig.height=10, fig.width=14}
path <- "../03processed-data/apsimxFiles/ModifiedSKL_0.11AshleyDeneSD1.db"
dt_pred07 <- autoapsimx::read_dbtab(path = path, "Report")
dt_pred07
dt_obs <- readd(SWC_mean)
site_sd <- autoapsimx::extract_trts(path)
dt_obs = dt_obs[Experiment == site_sd[1] & SowingDate == site_sd[2]]
pred_obs = manipulate(DT_obs = dt_obs, DT_pred = dt_pred07)
test
palette = rep("grey", times = 2)
             
palette_named = setNames(palette,  c("PSWC", "SWC"))
palette_named[2] = "red"
point_size = 2
pred_obs[, KLR_RFV := paste0("klReduction=", KLR, "\r\n", "RFV=", RFV)] %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = PSWC, color = "PSWC"), size = point_size) +
  geom_point(aes(y = SWC,color = "SWC"), size = point_size) +
  facet_wrap(~ KLR_RFV) +
  ggtitle(paste0("Surface kl = ", unique(pred_obs$SKL))) +
  theme_water() +
  scale_x_date(date_labels = "%Y %b") +
  scale_color_manual(name = "", values = palette_named) +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 30, hjust = 1))

```
# Subset to the best NSE

```{r}
best_NSE
pred_obs$SKL %>% unique()
bestfit= pred_obs[KLR == best_NSE$KLR[1] &
                    RFV == best_NSE$RFV[1] ] 
bestfit %>% 
  ggplot(aes(Date, PSWC)) +
  geom_point(color = "grey") +
  geom_point(aes(y = SWC), color = "red")
```

# EDA SD1 with all SKL 
```{r}

test = DT_stats[, unlist(stats, recursive = FALSE),
                by = key(DT_stats)
                ]
top5_stats = test[ NSE > 0 
                   ][order(NSE,R2, RMSE, decreasing = TRUE),
                     index := seq_len(.N), 
                     by = list(Experiment, SowingDate)
                     ][index <= 5][, index := NULL][]

top5_stats[Experiment %like% "Ashley"]$SowingDate %>% unique() 
top5_stats[Experiment %like% "Iver"]$SowingDate %>% unique() 

DT_stats_sub = DT_stats[top5_stats, 
                        on = c("Experiment", "SowingDate", "SimulationID", "KLR", "RFV", "SKL")]

top5 = DT_stats_sub[, unlist(data, recursive = FALSE), 
                    by = list(Experiment, SowingDate, KLR, RFV, SKL, NSE, R2, RMSE)]

```

```{r graph top5, fig.width=10, fig.height=10}
palette = rep("grey", times = 2)
             
palette_named = setNames(palette,  c("Predict SWC", "Observed SWC"))
palette_named[2] = "red"
point_size = 2
DT = top5[, KLR_RFV_SKL := paste0("klReduction=", KLR, 
                                  "\r\n", "RFV=", RFV,
                                  "\r\n", "SKL=", SKL)
           ][Experiment == "AshleyDene" & SowingDate == "SD5"] 
DT %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = PSWC, color = names(palette_named)[1]), size = point_size) +
  geom_point(aes(y = SWC,color = names(palette_named)[2]), size = point_size) +
  geom_text(aes(x = max(DT$Date) - 60, y = median(DT$PSWC), 
                label = paste0("NSE = ", NSE,
                                "\r\nR.square = ", R2,
                                "\r\nRMSE = ", RMSE)),inherit.aes = FALSE)+
  facet_grid(  KLR_RFV_SKL ~.) +
  ggtitle(paste0(unique(DT$Experiment), unique(DT$SowingDate))) +
  scale_x_date(date_labels = "%Y %b", date_breaks = "4 weeks") +
  scale_color_manual(name = "", values = palette_named) +
  theme_water() +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 30, hjust = 1))
```


## Iversen12 Sowingdates 9 and 10 have negative NSEs

EDA A BIT 
Seems there are too few observations in the SD10 in Iversen12
the prediction performance even worse than the using mean values 

```{r}
I12sd9and10 = DT_stats[Experiment %like% "Iver" &
                         SowingDate %in% c(paste0("SD", 9:10))]
I12sd9and10[, unlist(stats, recursive = FALSE), by = list(SowingDate, SimulationID, KLR, RFV, SKL)]
I12sd9and10$data[[1]] %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = PSWC, color = "PSWC"), size = point_size) +
  geom_point(aes(y = SWC,color = "SWC"), size = point_size) +
  # facet_wrap(~ KLR_RFV) +
  # ggtitle(paste0("Surface kl = ", unique(pred_obs$SKL))) +
  theme_water() +
  scale_x_date(date_labels = "%Y %b") +
  scale_color_manual(name = "", values = palette_named) +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 30, hjust = 1))
I12sd9and10[SowingDate == "SD9"]$data[[1]] %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = PSWC, color = "PSWC"), size = point_size) +
  geom_point(aes(y = SWC,color = "SWC"), size = point_size) +
  # facet_wrap(~ KLR_RFV) +
  # ggtitle(paste0("Surface kl = ", unique(pred_obs$SKL))) +
  theme_water() +
  scale_x_date(date_labels = "%Y %b") +
  scale_color_manual(name = "", values = palette_named) +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 30, hjust = 1))
```
What about ashley dene if the sd 9 and 10 so bad in iversen 12.
Seems much better even without look at the best fit parameters.


```{r}
I12sd9and10 = DT_stats[Experiment %like% "Ashley" &
                         SowingDate %in% c(paste0("SD", 9:10))]
I12sd9and10[, unlist(stats, recursive = FALSE), by = list(SowingDate, SimulationID, KLR, RFV, SKL)]
I12sd9and10$data[[1]] %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = PSWC, color = "PSWC"), size = point_size) +
  geom_point(aes(y = SWC,color = "SWC"), size = point_size) +
  # facet_wrap(~ KLR_RFV) +
  # ggtitle(paste0("Surface kl = ", unique(pred_obs$SKL))) +
  theme_water() +
  scale_x_date(date_labels = "%Y %b") +
  scale_color_manual(name = "", values = palette_named) +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 30, hjust = 1))
I12sd9and10[SowingDate == "SD9"]$data[[1]] %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = PSWC, color = "PSWC"), size = point_size) +
  geom_point(aes(y = SWC,color = "SWC"), size = point_size) +
  # facet_wrap(~ KLR_RFV) +
  # ggtitle(paste0("Surface kl = ", unique(pred_obs$SKL))) +
  theme_water() +
  scale_x_date(date_labels = "%Y %b") +
  scale_color_manual(name = "", values = palette_named) +
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 30, hjust = 1))
```


# What about each layers 

```{r}
SW_obs = readd(SW_mean)
SW_obs
DT_stats = readd(DT_stats)
DT_stats$data[[3]]
readd(dt)
DT = readd(pred_swc)
cols <- c("CheckpointID", "Experiment", "FolderName")
DT[, (cols) :=  NULL
   ][order(SimulationID)]

DT <- readd(pred_sw)
DT_STATS <- sims_stats(DT, col_pred = "SW(1)", col_obs = "i.SW(1)")
DT_STATS$data[[1]]
DT[, Zone := NULL]
grep("^(!?SW)", names(DT), value = TRUE)
setkeyv(DT, c("Date","Experiment", "SimulationID", "SowingDate",
              "KLR","RFV","SKL"))
key(DT)

DT %>% melt(id.vars = key(DT))


```

Might be easier to melt first and then join 
```{r}
dt <- readd(dt)
value_vars <- grep("^(!?SW\\()", names(dt), value = TRUE)
pred <- dt %>% 
  melt(value.name = "pred_VWC",
       measure.vars =value_vars, 
       variable.name = "Depth",
       variable.factor = FALSE)
cols <- c("CheckpointID", "Experiment", "FolderName", "Zone")
pred[, (cols) := NULL]
obs <- readd(obs_sd)
obs <- obs %>% 
  melt(value.name = "ob_VWC", 
       measure.vars =value_vars, 
       variable.name = "Depth",
       variable.factor = FALSE)
pred_obs <- merge.data.table(pred, obs, by.x = c("Date", "Depth"), by.y = c("Clock.Today", "Depth"))

TEST <- pred_obs[, list(data = list(.SD)), 
         by = c("Experiment", "SowingDate", "Depth","SimulationID")]
TEST <- sims_stats(pred_obs, keys = c("Experiment", "SowingDate", "Depth","SimulationID"),
           col_pred = "pred_VWC",
           col_obs = "ob_VWC")[]
TEST$stats[[1]]
```

```{r fig.height=14, fig.width=10}
# readd(DT_stats_SW)
DT = readd(pred_obs_pred_SW_Site_SD_AshleyDene_SD10_long_obs_SW_AshleyDene_SD10)
DT$Depth %>% 
  unique() %>% 
  factor(levels = paste0("SW(",1:22, ")"))
DT[, Depth := forcats::fct_relevel(as.factor(Depth), paste0("SW(",1:22, ")"))][]

point_size = 2
col_pred = "pred_VWC"
col_obs = "obs_VWC"
palette = rep("grey", times = 2)
palette_named = setNames(palette,  c(col_pred, col_obs))
palette_named[2] = "red"
DT %>% 
  ggplot(aes(Date)) +
        geom_point(aes(y = get(col_pred), color = names(palette_named)[1]), size = point_size) +
        geom_point(aes(y = get(col_obs), color = names(palette_named)[2]), size = point_size) +
        geom_text(aes(x = as.Date("2011-07-01"), y = median(DT[[col_pred]]),
                      label = paste0("NSE = ", NSE,
                                     "\r\nR.square = ", R2,
                                     "\r\nRMSE = ", RMSE)),inherit.aes = FALSE)+
        facet_grid( reformulate( "KLR_RFV_SKL", "Depth")) +
        ggtitle(paste0(unique(DT$Experiment), unique(DT$SowingDate))) +
        scale_x_date(date_labels = "%Y %b", date_breaks = "4 weeks") +
        scale_color_manual(name = "", values = palette_named) +
        theme_water() +
        theme(legend.position = "top",
              axis.text.x = element_text(angle = 30, hjust = 1))
  
  plot_params("../05figures/TEST.PNG", col_pred = "pred_VWC", col_obs = "obs_VWC", Depth = "Depth")
```
# Out put top1 as a table 
```{r}

dt = readd(top5)
nested = dt[, list(data = list(.SD)), 
            by = .(Experiment, SowingDate, SimulationID, SKL,KLR, RFV, NSE, R2, RMSE)
            ][order(NSE, R2,RMSE)
              ][, .SD[1], by = .(Experiment, SowingDate)]
fwrite(nested[, data:=NULL], file = "../03processed-data/best_fitForSWC_Profile.csv")
nested
```

## Maybe use the top 5 to look at different layers? 
```{r}
readd(Site_SD_AshleyDene_SD3)
readd(top5)
DT = readd(DT_stats)
DT$data[[1]]
```

# Layerbylayer Calibration 

Plan develop

```{r}
path <-"../03processed-data/apsimxFilesLayers/"
dbs <- list.files(path, pattern = "*.db$", full.names = TRUE)

```

`sims_stats.R` function development 
```{r}
db <- "../03processed-data/apsimxFilesLayers/LayerKL_0.065RFV_15Iversen12SD1.db"
# db <- "LayerKL_0.01RFV_15AshleyDeneSD10L2kl0.01.db"
pred_I12SD1 <- read_dbtab(db, table = "Report")
layerNo. <- regmatches(basename(db), regexpr("L\\d{1,2}", basename(db)))
if(length(layerNo.) == 0){
  layerNo. <- as.character("L1")
}
layer <- gsub("(L)(\\d{1,2})", "SW\\\\(\\2\\\\)", layerNo.)
depth_int <- as.integer(gsub("L", "", layerNo.))
colsofInteresetd <- grep(pattern = layer, colnames(pred_I12SD1), value = TRUE)
keys <- grep("SW", colnames(pred_I12SD1), invert = TRUE, value = TRUE)
cols <- c(keys, colsofInteresetd)
pred <- pred_I12SD1[,..cols
                    ][, Depth := depth_int]
data.table::setnames(pred, colsofInteresetd, "pred_VWC")
obs_I12SD1 <- readd(obs_SW_Iversen12_SD1)
keys_obs <- grep("SW", colnames(obs_I12SD1), invert = TRUE, value = TRUE)
cols <- c(keys_obs, colsofInteresetd)
obs <- obs_I12SD1[,..cols
                    ][, Depth := depth_int]
data.table::setnames(obs, colsofInteresetd, "ob_VWC")

pred_obs <- data.table::merge.data.table(pred, obs,
                                         by.x = c("Date", "Depth"),
                                         by.y = c("Clock.Today", "Depth"))
stats <- sims_stats(pred_obs,
                    keys = c("Experiment", "SowingDate", "Depth"),
                    col_pred = "pred_VWC",
                    col_obs = "ob_VWC")
# pred_I12SD1 %>%
#   data.table::melt(value.name = "pred_VWC",
#                    measure.vars = colsofInteresetd,
#                    variable.name = "Depth",
#                    variable.factor = FALSE)
# pred_obs <- manipulate(obs_I12SD1, redundant_cols = c("CheckpointID", "Zone"), DT_pred = pred_I12SD1)
# 
# 
# pred_obs

# pred_obs[, Layer := layerNo.]
# is.data.table(pred_obs)
# sims_stats(pred_obs = pred_obs, keys = c("Experiment", "SowingDate", "Layer"), col_pred = "SW(2)", col_obs =  "i.SW(2)")[]
# setkeyv(pred_obs, keys)
# nested <- pred_obs[, list(data = list(.SD)), by = key(pred_obs)]
# hydroGOF::gof(pred_obs$`SW(2)`, pred_obs$`i.SW(2)`)

pred_obs %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = ob_VWC), col = "red")+
  geom_point(aes(y = pred_VWC))
```

`sims_stats` function test 

```{r}
DT = readd(SW_mean)
l <- autoapsimx::sims_stats_multi(path_sims = "../03processed-data/apsimxFilesLayers/", pattern = "^Layer.+.db$", DT_observation = DT, mode = "Manual", keys = c("Experiment", "SowingDate", "Depth"), test = TRUE)
```


# Test the visulisation 
2 sites * 18 sowingdates * 21 depths = 756 sims


```{r}
DT = readd(DT_stats_layerKL)
# Add a new simID as unique identifier, otherwise the unlist won't work correctly. 

DT[, SimsID := 1:nrow(DT)]
unnest <- DT[, unlist(data, recursive = FALSE), by = .(Experiment, SowingDate, Depth, SimsID)]
unnest$SKL %>% unique() %>% length()
unnest
unnest_stats <- DT[, unlist(stats, recursive = FALSE), by = .(Experiment, SowingDate, Depth, SimsID)]
renest <- unnest_stats[,.(NSE, R2, RMSE) , by =.(Experiment, SowingDate, Depth, SimsID)
                       ][, list(stats_renest = list(.SD)), by =.(Experiment, SowingDate, Depth)]
renest[, stats_renest := lapply(stats_renest, function(x){
  x[NSE > 0 # Pointless to have NSE value less than 0
    ][order(NSE,R2, RMSE, decreasing = TRUE),
      index := seq_len(.N),
      by = list(SimsID)
      ][index < 5][, index := NULL]
  x
})]

ADSD2 <- DT[Experiment == "AshleyDene" & SowingDate == "SD2" & Depth == "2"]
ADSD2 <- ADSD2[, unlist(data, recursive = FALSE) , by = .(Experiment, SowingDate, Depth, SimsID)]
ADSD2$SKL %>% unique()
```
# Things are not right because  
1. skl is still the surface kl in the current calculation DT  
2. Simulations have only detachted kl in different layers  

**Need to redesign the workflow** 

logic:  
1. take the best fit of SKL and edit them into 18 simulations files 
2. generate 18 * 11 simulation files for the second layer   
3. calculate the stats in the second layer and decide the best fit   
4. use the best fit in second layer and change thrid layer 
5. and so forth 

### what is the best fit in first layer

```{r}
DT = readd(top5)
DT$SimulationID %>% unique() %>% length()
DT$Experiment %>% unique() %>% length()
DT$SowingDate %>% unique() %>% length()
DT$KLR %>% unique() %>% length()
DT$SKL %>% unique() %>% length()
dt = readd(top5)
nested = dt[, list(data = list(.SD)), 
            by = .(Experiment, SowingDate, SimulationID, SKL,KLR, RFV, NSE, R2, RMSE)
            ][order(NSE, R2,RMSE)
              ][, .SD[1], by = .(Experiment, SowingDate)]

nested[Experiment %like% "Ash" & SowingDate == "SD2"]
```

## Reconstruct the apsimx file name to extract from the 440 files 

lesson from poor starting design 

```{r}
info = nested[,.(Experiment, SowingDate, SimulationID, SKL, KLR,RFV)]

files = sapply(seq(1, nrow(info)), function(x){
  paste0("ModifiedSKL_", info[x, ][["SKL"]], info[x, ][["Experiment"]], info[x, ][["SowingDate"]], ".apsimx")
})
# info[1, ][["Experiment"]]
# info[1, ][["SowingDate"]]
# info[1, ][["SKL"]]
file1 = file.path(here::here("03processed-data/apsimxFiles/"), files[1])
fileTo = file.path(here::here("03processed-data/"))
system(paste("cp", file1, fileTo))
```
## Retrive the kl values for layer 2 to 22 in the best fit 

Another lesson:  ** Didn't even put a kl there**

```{r}
 files = lapply(seq(1, nrow(info)), function(x){
    orig = here::here("03processed-data/apsimxFiles/")
    copyto = here::here("03processed-data/apsimxFilesLayers/")
    basename = paste0("ModifiedSKL_", 
                      info[x, ][["SKL"]],
                      info[x, ][["Experiment"]], 
                      info[x, ][["SowingDate"]], ".db")
    file = file.path(orig, basename)
    dt = read_dbtab(file, "SummaryNumbers")
    dt[, ':='(Experiment = info[x, ][["Experiment"]],
              SowingDate = info[x, ][["SowingDate"]],
              SKL = info[x, ][["SKL"]])]
    
    dt = dt[SimulationID == info[x, ][["SimulationID"]]]
  })
# info
DT = rbindlist(files)
colnames(DT)
setkeyv(DT, c("Experiment", "SowingDate", "SKL", "RFV"))
value_vars = grep("KLmod", colnames(DT), value = TRUE)
id_vars = data.table::key(DT)
cols = c(id_vars, value_vars)
DT_long = DT[,..cols] %>% 
  melt(id.vars = id_vars, 
       measure.vars = value_vars)
DT_long[, ':='(Layer = gsub("\\D", "", variable),
               kl = SKL * value)][]
DT_long$kl %>% range()
DT_long[Experiment %like% "Ash" & SowingDate == "SD2"]
```

can a kl value as low as 0.00015??

### STEP 1 Get the apsimx files with the correct initial conditions
```{r}

```

### STEP 2 Modified them with the best fit SKL and the results from the expotential decay

### STEP 3 Modified the `best fit` apsimx files to cover more kl values from layer 2 

### STEP 4 Run


### STEP 5 Visual best fit 

```{r, fig.height=14, fig.width=8}
DT = readd(DT_stats_layerKL)
stats = DT[, Source:=basename(Source)
           ][order(Experiment, SowingDate, Depth)]
stats$Depth %>% range()
top3 = stats[, unlist(stats, recursive = FALSE), by =.(Source, Experiment, SowingDate, Depth)
               ][Depth != 1 
                 # & NSE > 0 
                 ][order(NSE,R2, RMSE, decreasing = TRUE),
                   index := seq_len(.N), 
                   by = list(Experiment, SowingDate,Depth)
                   ]

JOINNED = stats[top3[index == 1], on = "Source"
                ][, unlist(data, recursive = FALSE), 
                  by = .(Source, Experiment, SowingDate, Depth)
                  ][, kl := regmatches(Source, regexpr("kl0\\.\\d{1,3}", Source, perl = TRUE))]

id = JOINNED$Source %>% unique()
top1stats = stats[Source %in% id
                  ][, unlist(stats, recursive = FALSE), 
                    by = .(Source, Experiment, SowingDate, Depth)]
JOINNED_stats = top1stats[JOINNED, on = "Source"]
adsd2 = JOINNED_stats[Experiment == "AshleyDene" & SowingDate == "SD2"
                      ][order(Depth)] 
adsd2 %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = ob_VWC), col = "red")+
  geom_point(aes(y = pred_VWC)) +
  # geom_point(aes(y = RootDepth/10000), col = "green") +
  facet_grid( Depth ~ kl) +
  
  ggtitle("Overview of the kl values distribution for", 
          subtitle = paste(unique(adsd2$Experiment), unique(adsd2$SowingDate)))

adsd2[, ':='(NSE = paste0("NSE=\r\n",NSE), 
             R2 = paste0("R2=\r\n", R2),
             RMSE = paste0("RMSE=\r\n", RMSE))] %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = ob_VWC), col = "red")+
  geom_point(aes(y = pred_VWC)) +
  # geom_point(aes(y = RootDepth/10000), col = "green") +
  facet_grid( Depth + kl + NSE + RMSE + R2 ~ .) +
  
  ggtitle("Overview of the kl values distribution for", 
          subtitle = paste(unique(adsd2$Experiment), unique(adsd2$SowingDate)))

```

#### TEST THE SUBSET_STATS FUNCTION
```{r}
DT = readd(DT_stats_layerKL)
DT = subset_stats(DT)
DT[, .(Experiment, SowingDate )] %>% unique()
plot_params(DT, )
```

```{r}
skl_best_fit = readd(best_fit)
skl_best_fit = skl_best_fit[,.(Experiment, SowingDate, kl = SKL, Depth = 1L)]
DT = readd(best_fit_layers)
DT[,kl := as.numeric(gsub("kl","", kl))]
kl_best_fit = unique(DT[, .(Experiment, SowingDate, Depth, kl)])
best_fit_layerkl = rbindlist(list(skl_best_fit, kl_best_fit), use.names = TRUE)
setkey(best_fit_layerkl, Experiment, SowingDate, Depth)
best_fit_layerkl
```


#### fill the best fit back to the model - PLAN IS NOT WORKING SO THIS IS THE ALTERNATIVE QUICK FIX
```{r, fig.width=10, fig.height=17}
# process ob 

palette = rep("grey", times = 2)
palette_named = setNames(palette,  c("pred_VWC", "obs_VWC"))
palette_named[2] = "red"
dbs = list.files("../03processed-data/bestfitLayerkl/", pattern = ".db$", full.names = TRUE)
# l_p <- vector("list", length = length(dbs))
# names(l_p) = dbs
Sites <- c("AshleyDene", "Iversen12")
dt_sw = readd(SW_mean)
sds = unique(dt_swc$SowingDate)
for(i in Sites){
  for(j in sds){
    db = grep(paste0(i, j,".db"), x = dbs, value = TRUE)
    OBS = dt_sw[Experiment == i & SowingDate == j]
    PREDS = read_dbtab(db, table = "Report")
    value_vars = readd(value_vars)
    pred_SW = data.table::melt(PREDS,
                               value.name = "pred_VWC",
                               measure.vars = value_vars,
                               variable.name = "Depth",
                               variable.factor = FALSE)
    long = data.table::melt(OBS,
                            value.name = "obs_VWC",
                            measure.vars =value_vars,
                            variable.name = "Depth",
                            variable.factor = FALSE)
    pred_obs = merge.data.table(pred_SW[,(c("CheckpointID", "Experiment", "FolderName","Zone")) := NULL],
                 long, 
                 by.x = c("Date", "Depth"), 
                 by.y = c("Clock.Today", "Depth"))[, Depth := forcats::fct_relevel(as.factor(Depth),                                                                                   paste0("SW(",1:22,")"))]

p1 = pred_obs %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = obs_VWC, col = "obs_VWC"))+
  geom_point(aes(y = pred_VWC, col = "pred_VWC")) +
  # geom_point(aes(y = RootDepth/10000), col = "green") +
  facet_grid( Depth ~ .)  +
  ggtitle(paste0(unique(pred_obs$Experiment), unique(pred_obs$SowingDate))) +
       scale_x_date(date_labels = "%Y %b", date_breaks = "4 weeks") +
       scale_color_manual(name = "", values = palette_named) +
       theme_water() +
       theme(legend.position = "top",
             axis.text.x = element_text(angle = 30, hjust = 1))

ggsave(paste0("C:/Data/Master/05figures/kl_LayerByLayerCalibrationEDA/", basename(db), ".png"), p1, dpi = 300, height = 14, width = 8)

  }
}

```
swc

```{r}
dt_swc = readd(SWC_mean)

for(i in Sites){
  for(j in sds){
    db = grep(paste0(i, j,".db"), x = dbs, value = TRUE)
    OBS = dt_swc[Experiment == i & SowingDate == j]
    PREDS = read_dbtab(db, table = "Report")
    value_vars = readd(value_vars)
    pred_obs = merge.data.table(PREDS[,(c("CheckpointID", "Experiment", "FolderName","Zone")) := NULL],
                     OBS, 
                     by.x = c("Date"), 
                     by.y = c("Clock.Today"))
    palette = rep("grey", times = 2)
    palette_named = setNames(palette,  c("PSWC", "SWC"))
    palette_named[2] = "red"
    p2 = pred_obs %>% 
      ggplot(aes(Date)) +
      geom_point(aes(y = PSWC, col = "PSWC"))+
      geom_point(aes(y = SWC, col = "SWC")) +
      ggtitle(paste0(unique(pred_obs$Experiment), unique(pred_obs$SowingDate))) +
           scale_x_date(date_labels = "%Y %b", date_breaks = "4 weeks") +
           scale_color_manual(name = "", values = palette_named) +
           theme_water() +
           theme(legend.position = "top",
                 axis.text.x = element_text(angle = 30, hjust = 1))
    ggsave(paste0("C:/Data/Master/05figures/kl_LayerByLayerCalibrationEDA/", basename(db), "SWC.png"), p2, dpi = 300, height = 7, width = 10)
  }
}
```


```{r}
pred_obs %>% 
  ggplot(aes(Date)) +
  geom_point(aes(y = SWC), col = "red")+
  geom_point(aes(y = PSWC))

```


```{r}
bestfitkls = readd(best_fit_layerkl)
info = readd(info)
SW_DUL_LL = readd(SW_DUL_LL)
SD_tidied = readd(SD_tidied)
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
source("../02scripts/R/EditApsimxCalibrateLayers.R")
EditApsimxLayers(path = apsimx, info = info, SW_DUL_LL = SW_DUL_LL, SD_tidied = SD_tidied, kls = bestfitkls)
```


```{r}
path <- "../03processed-data/apsimxFiles/"
path_dbs = list.files("../03processed-data/apsimxFiles/", ".+Ashley.+SD1.db$", full.names = TRUE)
l_obs = lapply(path_dbs, function(x) read_dbtab(x, "Report"))
SD1_SKLs = rbindlist(l_obs)

```

