---
title: "Data_EDA"
author: "jian (AKA Frank) liu"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 10, fig.height = 7, dpi = 300)
options(scipen = 999)
source("../02scripts/R/packages.R")
```

# Protocol

- Load data from sqlite   
- Set constants. e.g. colours and keys  
- Set target  
    Key outcomes:   
    - Initial soil water content[Initial soil water]      
    - A set of DUL[DUL AND LL]  
    - A set of LL[DUL AND LL]  
- Calculation and summarising  
- Joining[Combine Soil Paras]  
- Set up directory structure[Set directory structure]  
- Invoke **Edit**  [Invoke Apsimx]  

# File structure 

```{r}
# Environmental variables to control file paths
Sys.setenv("WorkingDir" = here::here())
Sys.setenv("BaseApsimxDir" = file.path(Sys.getenv("WorkingDir"), "01raw-data/ApsimxFiles/"))
Sys.setenv("MetDir" = file.path(Sys.getenv("WorkingDir"), "01raw-data/ClimateAndObserved/"))
Sys.setenv("ConfigFileDir" = file.path(Sys.getenv("WorkingDir"), "03processed-data/ConfigurationFiles/"))
Sys.setenv("CoverDataDir" = file.path(Sys.getenv("WorkingDir"), "03processed-data/CoverData/"))
Sys.setenv("SimsDir" = file.path(Sys.getenv("WorkingDir"), "03processed-data/apsimxFiles/"))
## Verifcation
# Sys.getenv("MetDir")
# list.files(Sys.getenv("SimsDir"))

```

# 20200720 Edit 2nd layer of best slurp to do one layer optimisation 

```{r}
nodes = readLines("../01raw-data/ApsimxFiles/LucerneBaseConfigTemplate")
layernode = nodes[2]

SowingDates = readd(SD_tidied)
SDs = unique(SowingDates$SD)
Countries = "NewZealand"
Locations = unique(SowingDates$Experiment)
KL_range <- seq(0.005, 0.11, by = 0.005)
# Could be defined on the fly 
KL_layers <- 21L


Edit_singalLayer <- function(Countries. = Countries,
                             Locations. = Locations, 
                             SDs. = SDs, 
                             kl, 
                             nodes = layernode, 
                             layberNo. = 2, 
                             outdir = "../03processed-data/ConfigurationFiles/"){
  nodes = gsub("\\s=\\s", paste0("[", layberNo., "]", " = "), layernode)
  ll = vector("list", length = length(Countries) * length(Locations) *length(SDs))
  pos = 1
  for(Country in Countries.){
    for(Location in Locations.){
      for(SD in SDs.){
        names(ll)[[pos]] = paste0(Country, ".", Location, ".", SD)
        # print(Country);print(Location);print(SD)
        nodepath = gsub("Country", Country, nodes)
        nodepath = gsub("Location", Location, nodepath)
        nodepath = gsub("SDXX", SD, nodepath)
        v = vector("character", length = length(nodepath))
        # Parameters and values
        ll[[pos]] = paste0(nodepath, kl)
        pos = pos + 1
        f <- file(paste0(outdir, "Layer_", layberNo., "kl_", kl,".txt"), "w")
        # Write values into the file 
        cat(unlist(ll, recursive = FALSE, use.names = FALSE), "\r",
            sep = "\r", 
            file = f, 
            append = TRUE)
        # Close the file and clean it from memory 
        close(f)
        rm(f)
        gc()
      }
    }
  }
  }
```

```{r output configuration files for 2nd layer}
for( i in KL_range){
  Edit_singalLayer(kl = i)
}

```
```{r Edit 2nd layer kl in Lucerne apsimx}
layberNo. = 2
# Constants 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_Basefile <- file.path("../03processed-data/apsimxLucerne/Bestslurpkls2nd.apsimx")

apsimx_sims_dir <- file.path(Sys.getenv("WorkingDir"), "/03processed-data/apsimxFilesLayers/")

for (kl in KL_range){
       # Edit the base apsimx file and save it to a new name
       ## modify the apsimx file
       modifiedName <- paste0("../03processed-data/apsimxFilesLayers", "/Layer_", layberNo., "kl_", kl,".apsimx")
       system(paste("cp", apsimx_Basefile, modifiedName))
       system(paste(apsimx, modifiedName, apsimx_flag, paste0(Sys.getenv("ConfigFileDir"), "/Layer_", layberNo., "kl_", kl,".txt")))

     }

```

need a minimum plan to run the optimisation

```{r 2nd layer optimisation development}
dbs = list.files("../03processed-data/apsimxFilesLayers/", 
                 pattern = "Layer_2.+.db$", full.names = TRUE)
tab = read_dbtab(dbs[1], "PredictedObserved")
colnames(tab)
layer2 = tab[,.(Observed.Experiment,Observed.SowingDate,Clock.Today, 
                `Predicted.SW(2)`, `Observed.SW(2)`)]
p = layer2 %>% 
  ggplot(aes(Clock.Today, `Predicted.SW(2)`))+
  geom_line()+
  geom_point(aes(y =  `Observed.SW(2)`), color = "red")+
  facet_wrap(Observed.Experiment~Observed.SowingDate)
stats = hydroGOF::gof(sim = layer2[["Predicted.SW(2)"]], obs = layer2[["Observed.SW(2)"]])
transpose(as.data.table(stats, keep.rownames = T), make.names = "rn")
```

```{r}
read_subsetLayer <- function(layerNo. = 2, 
                             path = "../03processed-data/apsimxFilesLayers/"){
  layerNo. = layerNo.
  pattern = paste0("Layer_", layerNo., ".+.db$")
  dbs = list.files(path, pattern = pattern, full.names = TRUE)
  col_pred = paste0("Predicted.SW(", layerNo., ")")
  col_obs = paste0("Observed.SW(", layerNo., ")")
  cols = c("Observed.Experiment","Observed.SowingDate","Clock.Today", 
           col_pred, col_obs)
  tab = lapply(dbs, function(x){
    tab = read_dbtab(x, "PredictedObserved")
    layer2 = tab[,..cols]
  })
}

tabs = read_subsetLayer()
names(tabs) = dbs
lapply(names(tabs) , function(x){
  p = tabs[[x]] %>% 
    ggplot(aes(Clock.Today, `Predicted.SW(2)`))+
    geom_line()+
    geom_point(aes(y =  `Observed.SW(2)`), color = "red")+
    facet_wrap(Observed.Experiment~Observed.SowingDate)
  ggsave(filename = file.path("../05figures/kl_LayerByLayerCalibrationEDA/",
                            paste0(basename(x), ".png")), plot = p, device = "png",
       dpi = 300, height = 9, width = 12)
})
tab_stats = lapply(tabs,function(x){
  stats = hydroGOF::gof(sim = x[[col_pred]], obs = x[[col_obs]])
  transpose(as.data.table(stats, keep.rownames = T), make.names = "rn")
})
tab_stats =rbindlist(tab_stats, idcol = "source")
bestfit = tab_stats[order(NSE,r, RMSE, MAE, decreasing = TRUE)]$source[1]
bestfitkl = as.numeric(regmatches(basename(bestfit), 
                                regexpr("0\\.\\d{2,3}", 
                                        basename(bestfit))))
cat("The best fit kl for 2nd layer is", bestfitkl, ".\r\n")
theapsimx = gsub("\\.db$", ".apsimx", bestfit)
if(isTRUE(file.exists(theapsimx))){
  cat("Found the right apsimx file -", theapsimx)
}
```
```{r}
layberNo. = 3
# Constants 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_Basefile <- file.path(theapsimx)

apsimx_sims_dir <- file.path(Sys.getenv("WorkingDir"), "/03processed-data/apsimxFilesLayers/")

for (kl in KL_range){
       # Edit the base apsimx file and save it to a new name
       ## modify the apsimx file
       modifiedName <- paste0("../03processed-data/apsimxFilesLayers", "/Layer_", layberNo., "kl_", kl,".apsimx")
       system(paste("cp", apsimx_Basefile, modifiedName))
       system(paste(apsimx, modifiedName, apsimx_flag, paste0(Sys.getenv("ConfigFileDir"), "/Layer_", layberNo., "kl_", kl,".txt")))

     }
```


# 20200701 Edit slurp kls into apsimx lucerne 

**Because the best fit kls are not yet the best**

1. Need the best parameter combination.  
2. Extract the percentage reduction of surface kls from the `SummaryNumber` in the db.  
3. Calculate the artifical kls. 

```{r}
nodes = readLines("../01raw-data/ApsimxFiles/LucerneBaseConfigTemplate")
loadd(info)
dbs = list.files("../03processed-data/apsimxFiles/", pattern = "*.db$")
loadd(kls) # This is the best kls from slurp model
kls[, kl := round(kl, digits = 3)]
```

```{r}
InitialConds = readd(SW_DUL_LL)
SowingDates = readd(SD_tidied)
SDs = unique(SowingDates$SD)
Countries = "NewZealand"
Locations = unique(SowingDates$Experiment)
ll = vector("list", length = length(Countries) * length(Locations) *length(SDs))
pos = 1
for(Country in Countries){
  for(Location in Locations){
    for(SD in SDs){
      names(ll)[[pos]] = paste0(Country, ".", Location, ".", SD)
   
      # print(Country);print(Location);print(SD)
      nodepath = gsub("Country", Country, nodes)
      nodepath = gsub("Location", Location, nodepath)
      nodepath = gsub("SDXX", SD, nodepath)
      v = vector("character", length = length(nodepath))
      # 
      # Parameters and values
      SW = InitialConds[Experiment == Location & SowingDate == SD]$SW
      kl = kls[Experiment == Location & SowingDate == SD]$kl
      LL = InitialConds[Experiment == Location & SowingDate ==SD]$LL
      LL15 = LL
      AirDry = LL
      DUL = InitialConds[Experiment == Location & SowingDate ==SD]$DUL
      SAT = DUL
      # # The order is critical - fix me? remove the order hurdle
      v = c(paste0(SW, collapse = ","),
            paste0(kl, collapse = ","),
            paste0(LL, collapse = ","),
            paste0(LL15, collapse = ","),
            paste0(AirDry, collapse = ","),
            paste0(DUL, collapse = ","),
            paste0(SAT, collapse = ","))
      ll[[pos]] = paste0(nodepath, v)
      pos = pos + 1
      
    }
  }
}



f <- file(paste0(Sys.getenv("ConfigFileDir"),"/Bestslurpkls.txt"), "w")
# Write values into the file 
cat(unlist(ll, recursive = FALSE, use.names = FALSE), "\r",
   sep = "\r", 
   file = f, 
   append = TRUE)
# Close the file and clean it from memory 
close(f)
rm(f)
gc()
```

```{r Edit best layer kl in Lucerne apsimx}


# Constants 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_Basefile <- file.path(Sys.getenv("BaseApsimxDir"), "20200625LucerneBase.apsimx")
apsimx_sims_temp <- file.path(Sys.getenv("WorkingDir"), "03processed-data/apsimxLucerne/temp.apsimx")
apsimx_sims_dir <- file.path(Sys.getenv("WorkingDir"), "03processed-data/apsimxLucerne/")
apsimx_config <- paste0(Sys.getenv("ConfigFileDir"),"/Bestslurpkls.txt")
modifiedName <- paste0(apsimx_sims_dir, "/Bestslurpkls2nd.apsimx")
system(paste('cp', apsimx_Basefile, modifiedName))


system(paste(apsimx, modifiedName, apsimx_flag, apsimx_config))
```


# 20200625 Edit best fit layers into apsimx lucerne 

```{r}
nodes = readLines("../01raw-data/ApsimxFiles/LucerneBaseConfigTemplate")
kls = fread("../03processed-data/best_fit_layerkls.csv")
InitialConds = readd(SW_DUL_LL)
SowingDates = readd(SD_tidied)
SDs = unique(SowingDates$SD)
Countries = "NewZealand"
Locations = unique(SowingDates$Experiment)
ll = vector("list", length = length(Countries) * length(Locations) *length(SDs))
pos = 1
for(Country in Countries){
  for(Location in Locations){
    for(SD in SDs){
      names(ll)[[pos]] = paste0(Country, ".", Location, ".", SD)
   
      # print(Country);print(Location);print(SD)
      nodepath = gsub("Country", Country, nodes)
      nodepath = gsub("Location", Location, nodepath)
      nodepath = gsub("SDXX", SD, nodepath)
      v = vector("character", length = length(nodepath))
      # 
      # Parameters and values
      SW = InitialConds[Experiment == Location & SowingDate == SD]$SW
      kl = kls[Experiment == Location & SowingDate == SD]$kl
      LL = InitialConds[Experiment == Location & SowingDate ==SD]$LL
      LL15 = LL
      AirDry = LL
      DUL = InitialConds[Experiment == Location & SowingDate ==SD]$DUL
      SAT = DUL
      # # The order is critical - fix me? remove the order hurdle
      v = c(paste0(SW, collapse = ","),
            paste0(kl, collapse = ","),
            paste0(LL, collapse = ","),
            paste0(LL15, collapse = ","),
            paste0(AirDry, collapse = ","),
            paste0(DUL, collapse = ","),
            paste0(SAT, collapse = ","))
      ll[[pos]] = paste0(nodepath, v)
      pos = pos + 1
      
    }
  }
}



f <- file(paste0(Sys.getenv("ConfigFileDir"),"/BestfitLayerkl.txt"), "w")
# Write values into the file 
cat(unlist(ll, recursive = FALSE, use.names = FALSE), "\r",
   sep = "\r", 
   file = f, 
   append = TRUE)
# Close the file and clean it from memory 
close(f)
rm(f)
gc()

# v = vector("character", length = length(nodepath))
# names(v) = nodepath
# i = "Iversen12"
# j = "SD1"
# kl = kls[Experiment == i & SowingDate == j]$kl
# 
# nodepath = gsub("Country", Country, nodes)
# nodepath = gsub("Location", Location[1], nodepath)
# nodepath = gsub("SDXX", "SD1",nodepath)
# nodepath = gsub("SDXX", "SD1",nodepath)
# 
# gsub("\\s$",  paste0(" ",kl,collapse = ","), v[grep("KL", names(v))])
# v[grep("KL", names(v))] = paste0(" ",kl,collapse = ",")
# paste0(names(v), v)
# names(v)
# paste0(names(v), v)
```


```{r Edit best layer kl in Lucerne apsimx}

t1 <- Sys.time()
# Constants 
apsimx <- "C:/Data/ApsimX/ApsimX/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_Basefile <- file.path(Sys.getenv("BaseApsimxDir"), "20200625LucerneBase.apsimx")
apsimx_sims_temp <- file.path(Sys.getenv("WorkingDir"), "03processed-data/apsimxLucerne/temp.apsimx")
apsimx_sims_dir <- file.path(Sys.getenv("WorkingDir"), "03processed-data/apsimxLucerne/")
apsimx_config <- paste0(Sys.getenv("ConfigFileDir"),"/BestfitLayerkl.txt")
modifiedName <- paste0(apsimx_sims_dir, "/BestfitLayerkl.apsimx")
system(paste('cp', apsimx_Basefile, modifiedName))


system(paste(apsimx, modifiedName, apsimx_flag, apsimx_config))



# for(Country in Countries){
#   for(Location in Locations){
#     for(SD in SDs){
#        # Edit the base apsimx file and save it to a new name
#        ## modify the apsimx file
#        modifiedName <- paste0(apsimx_sims_dir, "/BestfitLayerkl", Country, Location, SD, ".apsimx")
#        system(paste("cp", apsimx_sims_temp, modifiedName))
#        system(paste(apsimx, modifiedName, apsimx_flag, paste0(apsimx_config, Country, Location, SD,".txt")))
#        ## rename the modified one
#        # system(paste("mv", apsimx_sims_temp, paste0(apsimx_sims_dir, "/Modified", j, i, ".apsimx")))
#      }
#    }
# }
# ## delete the temp apsimx 
# system(paste("rm", paste0(apsimx_sims_dir, "/temp*")))
t2 <- Sys.time()
t2 - t1
```

# Construct kl ranges 
```{r}
KL_range <- seq(0.01, 0.11, by = 0.01)
# Could be defined on the fly 
KL_layer <- 22L
# length(SW_DUL_LL[Experiment == "AshleyDene" & SowingDate == "SD1"]$Depth)
# SKLs <- lapply(KL_range, function(x) rep(x, times = KL_layer))
# names(SKLs) <- KL_range

#BD 
DB_AshleyDene <- c("1.150,1.150,1.310,1.310,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950,1.950")
DB_Iversen12 <- c("1.260,1.260,1.260,1.440,1.440,1.440,1.570,1.570,1.570,1.580,1.580,1.580,1.580,1.590,1.590,1.590,1.590,1.590,1.590,1.590,1.590,1.590,1.590")

```

# ApsimX node paths 

```{r}

## The site level configuration 
weather = "[Weather].FileName = "
Height = "[SetCropVariables].Script.MaximumHeight = "
BD = "[Soil].Physical.BD = "
## The Sowing date level configuration 

SDnode = "[SlurpSowingRule].Script.SowingDate = "
ClockStart = "[Clock].Start = "

CoverData = "[SetCropVariables].Script.CoverFile = "
initialSW = "[Soil].InitialConditions.SW = "

DUL <- "[Soil].Physical.DUL = "
SAT <- "[Soil].Physical.SAT = "

AirDry <- "[Soil].Physical.AirDry = "
LL15 <- "[Soil].Physical.LL15 = "
LL <- "[Soil].Physical.SlurpSoil.LL = "

## The kl parameter level configuration 
KL <- paste0("[Soil].Physical.SlurpSoil.KL", "[1:", KL_layer,"]"," = ")

```

# Replacement values

```{r load data from cache}
drake::readd(SW_DUL_LL)
drake::readd(SD_tidied)
# Critical order
setkey(SW_DUL_LL, Experiment, SowingDate, Depth)
```

```{r}
t1 <- Sys.time()
# Constant
sites <- unique(SD_tidied$Experiment)
SDs <- paste0("SD", 1:10)

for (i in sites) {
  for (j in SDs) {
    
  # Site level
  ## met files 
  replacement_met <- file.path(Sys.getenv("MetDir"), paste0(i,".met"))
  ## Height
  replacement_MaxHeight <- ifelse(i == "AshleyDene", 390L, 595L)
  replacement_BD <- ifelse(i == "AshleyDene", DB_AshleyDene, DB_Iversen12)
  # Sowing date level 
  ## SD
  replacement_SD <- SD_tidied[Experiment == i & SD == j ]$Clock.Today
  ## ClockStart
  replacement_ClockStart <- paste0(replacement_SD, "T00:00:00")
  ## User provide light interception data 
  replacement_CoverData <- file.path(Sys.getenv("CoverDataDir"),paste0("CoverData", i, j, ".csv"))
  ## Soil parameters 
  replacement_initialSW <- SW_DUL_LL[Experiment == i & SowingDate == j]$SW
  replacement_DUL <- SW_DUL_LL[Experiment == i & SowingDate == j]$DUL
  replacement_SAT <- replacement_DUL
  replacement_LL <- SW_DUL_LL[Experiment == i & SowingDate == j]$LL
  replacement_AirDry <- replacement_LL
  replacement_LL15 <- replacement_LL
  
  ## The kl parameter level configuration 
  for (skl in KL_range){
    replacement_KL <- skl
    
    # Paste together ----
  
    apsimx_met <- paste0(weather, replacement_met)
    apsimx_Height <- paste0(Height, replacement_MaxHeight)
    apsimx_BD <- paste0(BD, replacement_BD)
    apsimx_SD <- paste0(SDnode, replacement_SD)
    apsimx_ClockStart <- paste0(ClockStart, replacement_ClockStart)
    apsimx_CoverData <- paste0(CoverData, replacement_CoverData)
    
    apsimx_initialSW <- paste0(initialSW, paste(replacement_initialSW,collapse = ","))
    apsimx_DUL <- paste0(DUL, paste(replacement_DUL,collapse = ","))
    apsimx_LL <- paste0(LL, paste(replacement_LL,collapse = ","))
    apsimx_KL <- paste0(KL, paste(replacement_KL,collapse = ","))
    apsimx_SAT <- paste0(SAT, paste(replacement_SAT,collapse = ","))
    apsimx_AirDry<- paste0(AirDry, paste(replacement_AirDry,collapse = ","))
    apsimx_LL15 <- paste0(LL15, paste(replacement_LL15,collapse = ","))
    
    # Write out ----
    f <- file(paste0(Sys.getenv("ConfigFileDir"),"/ConfigSKL_", skl[1], i, j, ".txt"), "w")
      # Write values into the file 
      cat(apsimx_met,
          apsimx_ClockStart,
          apsimx_Height,
          apsimx_BD,
          apsimx_SD,
          apsimx_CoverData,
          apsimx_initialSW,
          apsimx_DUL,
          apsimx_KL,
          apsimx_LL,
          apsimx_SAT,
          apsimx_AirDry,
          apsimx_LL15, "\r",
          sep = "\r", 
          file = f, 
          append = TRUE)
      # Close the file and clean it from memory 
      close(f)
      rm(f)
      gc()
    }

  }
}

t2 <- Sys.time()
t2 - t1
```
# Invoke Apsimx

```{r}
# Constants 
apsimx <- "C:/Data/ApsimX/ApsimX/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_Basefile <- file.path(Sys.getenv("BaseApsimxDir"), "20200517BaseSlurp.apsimx")
apsimx_sims_temp <- file.path(Sys.getenv("SimsDir"), "temp.apsimx")
apsimx_sims_dir <- Sys.getenv("SimsDir")
apsimx_config <- paste0(Sys.getenv("ConfigFileDir"),"/ConfigSKL_")
paste0(Sys.getenv("ConfigFileDir"),"/ConfigSKL_", skl[1], i, j, ".txt")
# Copy the base apsimx file to a temp file in a disposable dir
system(paste('cp', apsimx_Basefile, apsimx_sims_temp))
# system(paste(apsimx, apsimx_sims_temp, apsimx_flag, paste0(apsimx_config, sites[1], SDs[1],".txt")))

t1 <- Sys.time()
for(j in sites){
   for(i in SDs){
     for (skl in KL_range){
       # Edit the base apsimx file and save it to a new name
       ## modify the apsimx file
       modifiedName <- paste0(apsimx_sims_dir, "/ModifiedSKL_", skl, j, i, ".apsimx")
       system(paste("cp", apsimx_sims_temp, modifiedName))
       system(paste(apsimx, modifiedName, apsimx_flag, paste0(apsimx_config,  skl, j, i,".txt")))
       ## rename the modified one
       # system(paste("mv", apsimx_sims_temp, paste0(apsimx_sims_dir, "/Modified", j, i, ".apsimx")))
     }
   }
}
## delete the temp apsimx 
system(paste("rm", paste0(apsimx_sims_dir, "/temp*")))
t2 <- Sys.time()
t2 - t1
```


# Run all simulations 

```
..\ApsimX\ApsimX\Bin\Models.exe .\03processed-data\apsimxFiles\*.apsimx
```


.Simulations.LnP.Factors.Permutation.Manager.InitialKL
.Simulations.LnP.Factors.Permutation.KLR

Bulk density value is not correct in Iversen12. need a function to do this. 

Edit does not allow to access manager script? SOLVED IN ISSUE [#4905](https://github.com/APSIMInitiative/ApsimX/issues/4905#issuecomment-641614089)
```
System.Exception: Invalid path: .Simulations.LnP.LandPBase.Field.ManagerFolder.SetCropVariables.MaximumHeight
   at Models.Core.ApsimFile.EditFile.ApplyChanges(String apsimxFileName, List`1 factors) in C:\Data\ApsimX\ApsimX\Models\Core\ApsimFile\EditFile.cs:line 84
   at Models.Core.ApsimFile.EditFile.Do(String apsimxFilePath, String configFilePath) in C:\Data\ApsimX\ApsimX\Models\Core\ApsimFile\EditFile.cs:line 29
   at Models.Program.ModifyFile(String fileName, Boolean recurse) in C:\Data\ApsimX\ApsimX\Models\Main.cs:line 202
   at Models.Program.Main(String[] args) in C:\Data\ApsimX\ApsimX\Models\Main.cs:line 94
PS C:\Data\Master> ../ApsimX/ApsimX/Bin/Models.exe 03processed-data/apsimxFiles/temp.apsimx /Edit 03processed-data/ConfigAshleyDeneSD10.txt
System.Exception: Invalid path: .Simulations.LnP.LandPBase.Field.ManagerFolder.SlurpSowingRule.SowingDate
   at Models.Core.ApsimFile.EditFile.ApplyChanges(String apsimxFileName, List`1 factors) in C:\Data\ApsimX\ApsimX\Models\Core\ApsimFile\EditFile.cs:line 84
   at Models.Core.ApsimFile.EditFile.Do(String apsimxFilePath, String configFilePath) in C:\Data\ApsimX\ApsimX\Models\Core\ApsimFile\EditFile.cs:line 29
   at Models.Program.ModifyFile(String fileName, Boolean recurse) in C:\Data\ApsimX\ApsimX\Models\Main.cs:line 202
   at Models.Program.Main(String[] args) in C:\Data\ApsimX\ApsimX\Models\Main.cs:line 94
PS C:\Data\Master> ../ApsimX/ApsimX/Bin/Models.exe 03processed-data/apsimxFiles/temp.apsimx /Edit 03processed-data/ConfigAshleyDeneSD10.txt
PS C:\Data\Master> ../ApsimX/ApsimX/Bin/Models.exe 03processed-data/apsimxFiles/temp.apsimx /Edit 03processed-data/ConfigAshleyDeneSD10.txt
System.Exception: Invalid path: .Simulations.LnP.LandPBase.Field.ManagerFolder.SetCropVariables.CoverFile
   at Models.Core.ApsimFile.EditFile.ApplyChanges(String apsimxFileName, List`1 factors) in C:\Data\ApsimX\ApsimX\Models\Core\ApsimFile\EditFile.cs:line 84
   at Models.Core.ApsimFile.EditFile.Do(String apsimxFilePath, String configFilePath) in C:\Data\ApsimX\ApsimX\Models\Core\ApsimFile\EditFile.cs:line 29
   at Models.Program.ModifyFile(String fileName, Boolean recurse) in C:\Data\ApsimX\ApsimX\Models\Main.cs:line 202
   at Models.Program.Main(String[] args) in C:\Data\ApsimX\ApsimX\Models\Main.cs:line 94
```

# DEVELOPMENT 

```{r }
#Constants
outlier.colour = "#ff0000"
source("R/packages.R")
source("R/functions.R")
con <- dbConnect(SQLite(), "../03processed-data/Richard.sqlite3")
dbListTables(con)
SowingDates <- dbReadTable(con, "SowingDates") %>% 
  as.data.table()

```


```{r OverallAD, fig.cap='A boxplot shows the range of SWC in AshleyDene over 2 years.'}
water <- dbReadTable(con, "SoilWater", check.names = FALSE) %>% 
  as.data.table()

water[, ':='(Clock.Today = as.Date(Clock.Today))]
# [, SowingDate := factor(SowingDate, levels(SowingDate)[c(1,3:10, 2)])]
# Isolate SD 1 in AshleyDene
dbDisconnect(con)
# set key and make it order by dates and sowing date
setkey(water, Experiment, SowingDate, Clock.Today)
# water[, SWC:= NULL]
id_vars <- key(water)
value_vars <- grep("SW\\(\\d.+", colnames(water), value = TRUE)

```


# Initial soil water 

```{r}
SD <- SowingDates[, (c("AD", "I12")) := lapply(.SD, as.Date), .SDcols = c("AD", "I12")] %>% 
  melt(id.vars = "SD", 
       variable.name = "Experiment", value.name = "Clock.Today",
       variable.factor = FALSE) 
SD[, Experiment := ifelse(Experiment == "AD", "AshleyDene",  "Iversen12")]

SW_mean <- water[, lapply(.SD, mean, na.rm = TRUE), by = id_vars, .SDcols = value_vars]
SW_initials <- SW_mean[SD, on = c("Experiment", "SowingDate == SD", "Clock.Today"), roll = "nearest"]
SW_initials <- melt(SW_initials, 
                    id.vars = id_vars, variable.factor = FALSE,
                    variable.name = "Depth", value.name = "SW"
                    )[, ':='(SW = round(SW / 100, digits = 3))
                      ]

# kable(SW_initials, caption = "Initial soil water content in each layer in 10 sowing dates")%>%
#   kable_styling() %>%
#   scroll_box(width = "100%", height = "500px")
# Output the SW for different SDs
sites <- unique(SW_initials$Experiment)

```


# DUL AND LL

```{r}
# [SowingDate %in% paste0("SD", 1:5)]
DUL_LL <- water[, lapply(.SD, mean, na.rm = TRUE), 
                by = id_vars, .SDcols = value_vars # average 4 reps
                  ][, unlist(lapply(.SD, max_min), recursive = FALSE), 
                    by = .(Experiment, SowingDate), .SDcols = value_vars]

melted_DUL_LL <- melt(DUL_LL, 
                      id.var = c("Experiment","SowingDate"), 
                      variable.factor = FALSE) 
DUL_LL_SDs <- melted_DUL_LL[, (c("Depth", "variable")) := tstrsplit(variable, "\\.")] %>% 
  dcast(Experiment +  SowingDate + Depth ~ variable)

DUL_LL_SDsVWC <- DUL_LL_SDs[, ':='(DUL = round(DUL/100, digits = 3),
                                   LL = round(LL/100, digits = 3))
                            ][, PAWC := DUL - LL]
```


# Combine Soil Paras

```{r}
SW_DUL_LL <- SW_initials[DUL_LL_SDsVWC, on = c("Experiment", "SowingDate", "Depth")][Depth != "SW(2)"]

# Check if anything unusual 
SW_DUL_LL[DUL<SW]
SW_DUL_LL[LL>SW]

# Order the layers
SW_DUL_LL[, ':='(Depth = as.integer(gsub("\\D", "", Depth)),
                 SowingDate = fct_relevel(as.factor(SowingDate), paste0("SD", 1:10)))]
# order the order - CRITICAL 
setkey(SW_DUL_LL, Experiment, SowingDate, Depth)
# kable(SW_DUL_LL, caption = "Initial soil parameters for 22 layers in 10 different sowing dates.")%>%
#   kable_styling() %>%
#   scroll_box(width = "100%", height = "500px")

# save the processed table for 
```

# Explore the python system call 


```{python}
# import sqlite3
# import re
# import datetime
# import pandas as pd
# import numpy as np
# import matplotlib.pyplot as plt
# import os
# import math
```

_Test_
```{python test}
# con = sqlite3.connect('../03processed-data/Richard.sqlite3')
# mycur = con.cursor() 
# mycur.execute("SELECT name FROM sqlite_master WHERE type='table' ORDER BY name;")
# (mycur.fetchall())
```

Check the configuration data

```{python}
print(r.SW_DUL_LL)
SDs = ['SD' + str(SD) for SD in range(1, 11)]
SDs
sites = ['AshleyDene', 'Iversen12']
sites
```
```{python}

# for site in sites: 
#     for i in SDs:
#         r.SW_DUL_LL.loc[(r.SW_DUL_LL['Experiment'] == site) 
#                        & (r.SW_DUL_LL.SowingDate == i),:].drop_duplicates().to_csv('../03processed-data/Config' + site + i + '.csv',index = False)
```

_Note_  
Tried to use python to vectorised the data and output.  
seems not that easy to covert a column in pandas into a string.   
Back to R



# Testing

# Set directory structure

```{r}
t1 <- Sys.time()
#path to apsimx 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_file <- "C:/Data/Master/01raw-data/ApsimxFiles/20200520Demo.apsimx"
apsimx_sims_temp <- "C:/Data/Master/03processed-data/apsimxFiles/temp.apsimx"
apsimx_sims_dir <- "C:/Data/Master/03processed-data/apsimxFiles/"
apsimx_config <- "C:/Data/Master/03processed-data/configSoilWat"

# Node Path - copied from ApsimX UI

initialSW <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.InitialConditions.SW = "
DUL <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.DUL = "
LL <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.LucerneSoil.LL = "
LL15 <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.LL15 = "
# PAWC <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.PAWC = "
SAT <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.SAT = "
# Keys
sites <- unique(SW_DUL_LL$Experiment)
SDs <- paste0("SD", 1:10)

# Vectorise the values 
for(j in sites){
  for(i in SDs){
    # Filter the right values 
    SDsw <- SW_DUL_LL[SowingDate == i & Experiment == j]$SW
    SDDUL <- SW_DUL_LL[SowingDate == i & Experiment == j]$DUL
    SDLL <- SW_DUL_LL[SowingDate == i & Experiment == j]$LL
    apsimx_sw <- paste0(initialSW,
                        paste(SDsw,collapse = ","))
    apsimx_DUL <- paste0(DUL,
                         paste(SDDUL,collapse = ","))
    apsimx_LL <- paste0(LL,
                        paste(SDLL,collapse = ","))
    apsimx_LL15 <- paste0(LL15,
                          paste(SDLL,collapse = ","))
    apsimx_SAT <- paste0(SAT,
                         paste(SDDUL,collapse = ","))
    # Open a text file
    f <- file(paste0(apsimx_config, j, i, ".txt"), "w")
    # Write values into the file 
    cat(apsimx_sw,
        apsimx_DUL,
        apsimx_LL,
        apsimx_LL15,
        apsimx_SAT,"\r",
        sep = "\r", 
        file = f, 
        append = TRUE)
    # Close the file and clean it from memory 
    close(f)
    rm(f)
    gc()
  }

}

t2 <- Sys.time()
t2 - t1
```

# Invoke Apsimx

```{r}
t1 <- Sys.time()
for(j in sites){
   for(i in SDs){
     # Edit the base apsimx file and save it to a new name
     ## modify the apsimx file 
     system(paste(apsimx, apsimx_file, apsimx_flag, paste0(apsimx_config, j, i,".txt")))
     ## rename the modified one
     system(paste("cp", apsimx_file, paste0(apsimx_sims_dir, "Modified", j, i, ".apsimx")))
     ## delete the temp apsimx 
     # system(paste("rm", paste0(apsimx_sims_dir, "temp*")))
   }
  }
t2 <- Sys.time()
t2 - t1
```

```{r}
# system(apsimx)
t1 <- Sys.time()
# system(paste(apsimx, paste0(apsimx_sims_dir,"*.apsimx"), "/NumberOfProcessors:8"))
t2 <- Sys.time()
t2 - t1
```

It only takes 6 seconds for the apsimx ui to run 10 simulations. 