---
title: "APSIM_edit_fun"
author: "Junqi Zhu and Jian Liu"
date: "`r Sys.Date()`"
output: html_document
---

# Protocol

- Load data from sqlite   
- Set constants. e.g. colours and keys  
- Set target  
    Key outcomes:   
    - Initial soil water content[Initial soil water]      
    - A set of DUL[DUL AND LL]  
    - A set of LL[DUL AND LL]  
- Calculation and summarising  
- Joining[Combine Soil Paras]  
- Set up directory structure[Set directory structure]  
- Invoke **Edit**  [Invoke Apsimx]  


```{r setup, include=FALSE}
options(scipen=999)
  

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", 
                      fig.width = 10, fig.height = 7, dpi = 300)
#Constants
outlier.colour = "#ff0000"
source("R/packages.R")
source("R/EditApsimx.R")
```



# Set directory structure

```{r}
powerplant = TRUE
library(RLinuxModules)

if(isFALSE(powerplant)){
  
  #path to apsimx 
  apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
  apsimx_flag <- "/Edit"
  apsimx_file <- "C:/Data/Master/03processed-data/apsimxFiles/ModifiedSKL_0.06Iversen12SD2.apsimx"
  apsimx_sims_dir <- "C:/Data/Master/03processed-data/apsimxFiles/"
  apsimx_config <- "C:/Data/Master/03processed-data/ConfigurationFiles/"
} else{
  apsimxsif = "apsimx/2020.08.04.5350"
  module(paste("load", apsimxsif))
  module("load openlava")
  module("load asub/2.1")
  module ("load R/3.6.3")
  #Check loaded modules
  module("list")
  
  #Check if singularity working 
  system("apsimx-2020.08.04.5350.sif")
  apsimx <- "apsimx-2020.08.04.5350.sif"
  #Set up directories
  apsimx_flag <- "/Edit"
  apsimx_file <- here::here("03processed-data/apsimxFiles/ModifiedSKL_0.06Iversen12SD2.apsimx")
  apsimx_sims_dir <- here::here("03processed-data/apsimxFiles/")
  apsimx_config <- here::here("03processed-data/ConfigurationFiles/")
  apsimx_obs <- here::here("03processed-data/CoverData/")
  for(i in list(apsimx_sims_dir, apsimx_config,apsimx_obs)){
    if (!file.exists(i)) {
      cat("Creating the dir", i, "\r\n")
      dir.create(i)
    }
  }
}

```


# Prepare the configuration file and editting

**HAS BEEN TAKEN CARE IN THE PLAN_CONFIG**
# Test optimisation 
## Prepare the configuration on the fly
The DE optimisation will sample values from the range and 
change the parameter value on the fly and 
run the simulation to extract the pred-obs and 
return the best fit
Three parameters for configured slurp. 
```
config_KL = paste0("[Soil].Physical.SlurpSoil.KL", "[1:", KL_layer,"]"," = ")
config_iniKLR = "[SlurpSowingRule].Script.KLReductionFactor = "
config_iniRFV = "[SlurpSowingRule].Script.RFV = "
```
```{r}
source("R/optimisation.R")
```
ranges will be 
kl in between 0.005 and 0.11
KLR in between 0.0005 and 0.01 
RFV in between 10 and 35

# Test the optim function

```{r}
t1 = Sys.time()
#DEoptim
maxIt = 2
np = 3
KL_layer = 22
slurpnodes = c(paste0("[Soil].Physical.SlurpSoil.KL", "[1:", KL_layer,"]"," = "),
               "[SlurpSowingRule].Script.RFV = ",
               "[SlurpSowingRule].Script.KLReductionFactor = "
               )
lower = c(0.005, 10,  0.0005)
upper = c(0.11, 35, 0.01)
# The observaion value that will be used as the benchmark
obspara = "SWC"

opt.res =
  DEoptim::DEoptim(fn=cost.function, 
                   lower = lower,
                   upper = upper,
                   control=list(NP=np * 10, itermax=maxIt, parallelType=1,
                                storepopfrom = 1,
                                packages = c('RSQLite'),
                                parVar = c(
                                'slurpnodes',
                                'apsimx',
                                'apsimx_flag',
                                'apsimx_file',
                                'obspara',
                                'apsimx_sims_dir',
                                
                                'APSIMEditFun', 
                                'APSIMRun' ))
  )


save(opt.res, file =  file.path(apsimx_sims_dir,
                                paste0(Sys.Date(), 'opt.res', ".RData")))

fit.par = data.frame(estimates = opt.res$optim$bestmem, cost = opt.res$optim$bestval)

 
#output the statistical test
par = fit.par$estimates

write.csv(par, here::here("03processed-data/opt.par.csv"), row.names = F)
t2 = Sys.time()
t2-t1
```

# Submit to bsub

```{bash}
bsub -o optimisation_$$.log \
     -e optimisation_$$.err \
Rscript R/submitOptimJobs.R
```



# Optimise all 20 sowing dates 

```{r}
  #path to apsimx 
apsimx <- "C:/Data/ApsimX/ApsimXLatest/Bin/Models.exe"
apsimx_flag <- "/Edit"
# apsimx_file <- "C:/Data/Master/03processed-data/apsimxFiles/ModifiedSKL_0.06Iversen12SD2.apsimx"
apsimx_sims_dir <- "C:/Data/Master/03processed-data/apsimxFiles/"
# apsimx_config <- "C:/Data/Master/03processed-data/ConfigurationFiles/"
apsimxs = list.files(apsimx_sims_dir, pattern = ".apsimx$", full.names = T)
l_apsimxs = vector("list", length = length(apsimxs))
names(l_apsimxs) = apsimxs
t1 = Sys.time()
#DEoptim
maxIt = 200
np = 3
KL_layer = 22
slurpnodes = c(paste0("[Soil].Physical.SlurpSoil.KL", "[1:", KL_layer,"]"," = "),
               "[SlurpSowingRule].Script.RFV = ",
               "[SlurpSowingRule].Script.KLReductionFactor = "
               )
lower = c(0.005, 10,  0.0005)
upper = c(0.11, 35, 0.01)
# The observaion value that will be used as the benchmark
obspara = "SWC"


for( i in seq_len(length(l_apsimxs))){
  # The observaion value that will be used as the benchmark
  obspara = "SWC"
  apsimx_file = names(l_apsimxs)[[i]]
  opt.res = DEoptim::DEoptim(fn=cost.function, 
                             lower = lower,
                             upper = upper,
                             control=list(NP=np * 10, itermax=maxIt, parallelType=1,
                                          storepopfrom = 1,
                                          packages = c('RSQLite'),
                                          parVar = c(
                                            'slurpnodes',
                                            'apsimx', 
                                            'apsimx_flag',
                                            'apsimx_file',
                                            'obspara',
                                            'apsimx_sims_dir',
                                            'APSIMEditFun', 
                                            'APSIMRun' ))
                             )
  l_apsimxs[[i]] = opt.res
  filename = gsub("ModifiedSKL_0.06|.apsimx", "", basename(apsimx_file))
  save(opt.res, file =  file.path(apsimx_sims_dir,
                                  paste0(filename,'opt.res', ".RData")))
  fit.par = data.frame(estimates = opt.res$optim$bestmem, cost = opt.res$optim$bestval)
  #output the statistical test
  # par = fit.par$estimates 
  write.csv(fit.par, paste0(apsimx_sims_dir, filename,'opt.par.csv'), row.names = TRUE)
  }
t2 = Sys.time()
t2-t1

```

```{r}
opsresults = list.files("../03processed-data/apsimxFiles/", pattern = "\\.RData")
apsimxs = list.files(apsimx_sims_dir, pattern = ".apsimx$", full.names = T)
l_apsimxs = vector("list", length = length(apsimxs))
names(l_apsimxs) = apsimxs
```

```{r}
plot(opt.res, plot.type = "storepop")
```


```{r}
plot(opt.res, plot.type = "bestmemit")
plot(opt.res, plot.type = "storepop")
```


































It only takes 6 seconds for the apsimx ui to run 10 simulations. 