---
title: "kl estimation "
author: "jian (AKA Frank) liu"
date: "`r Sys.Date()`"
output: html_document
---

# Protocol

- Input data ready: met, cover and slurp `.apsimx`  
- Parameter ready: 
|Parameters|Units |Parameter levels tested |Description|
|:----|:----|:----|:----|
|RFV| mm/day| 10, 15, 20, 25, 30 and 35 |Maximum rate of root extension at 25 °C|
| $kl_{0}$|/day| 0.01, 0.03, 0.05, 0.07,0.09 and 0.11|Maximum kl value at surface layer(s)|
|$\lambda_{kl}$| dimensionless | −0.0005, −0.001,−0.002, −0.003,−0.005 and −0.01 | Exponential decay of kl0 with soil depth|  

- Set constant of key and values 

- Invoke **Edit**  [Invoke Apsimx]  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 10, fig.height = 7, dpi = 300)
#Constants
outlier.colour = "#ff0000"
source("R/packages.R")
source("R/functions.R")
con <- dbConnect(SQLite(), "../03processed-data/Richard.sqlite3")
dbListTables(con)
SowingDates <- dbReadTable(con, "SowingDates") %>% 
  as.data.table()

```


```{r subset}
biomass <- dbReadTable(con, "biomass", check.names = FALSE) %>% 
  as.data.table()
biomass[, ':='(Clock.Today = as.Date(Clock.Today))]
dbDisconnect(con)
# set key and make it order by dates and sowing date
setkey(biomass, Experiment, SowingDate, Clock.Today)
id_vars <- key(biomass)

LAI <- biomass[, .(LAImod), by = key(biomass)]
```


# Overview of the LAI
P88 in the thesis, 
LAI was calculated from $Specfic Leaf Area(SLA) \times TotalFW_{HarvestArea} \div 2000 $ 
```{r glimpse}

kable(LAI[1:50, ], caption = "Initial soil biomass content in each layer in 10 sowing dates")%>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")

```




```{r graphLAI, fig.height=10}
LAI[, SowingDate := fct_relevel(as.factor(SowingDate), paste0("SD", 1:10))] %>% 
  ggplot(aes(Clock.Today, LAImod, color = SowingDate)) +
  geom_point() +
  geom_hline(yintercept = 1, colour = "#ff0000") +
  facet_grid(SowingDate~ Experiment) +
  theme_water()

LAI_summaried <- LAI[, LAImod := ifelse(LAImod == 0, NA, LAImod) # Some values are 0 which should be NAs
                     ][, list(mean = mean(LAImod, na.rm = TRUE)), by = id_vars
                       ][!is.na(mean)]

LAI_summaried %>% 
  ggplot(aes(Clock.Today, mean, color = SowingDate)) +
  geom_point() +
  geom_hline(yintercept = 1, colour = "#ff0000") +
  facet_grid(SowingDate~ Experiment) +
  theme_water()
# Output the SW for different SDs
sites <- unique(SW_initials$Experiment)

```


# Combine Soil Paras

```{r}
SW_DUL_LL <- SW_initials[DUL_LL_SDsVWC, on = c("Experiment", "SowingDate", "Depth")][Depth != "SW(2)"]

# Check if anything unusual 
SW_DUL_LL[DUL<SW]
SW_DUL_LL[LL>SW]

# Order the layers
SW_DUL_LL[, ':='(Depth = as.integer(gsub("\\D", "", Depth)),
                 SowingDate = fct_relevel(as.factor(SowingDate), paste0("SD", 1:10)))]
# order the order - CRITICAL 
setkey(SW_DUL_LL, Experiment, SowingDate, Depth)
kable(SW_DUL_LL, caption = "Initial soil parameters for 22 layers in 10 different sowing dates.")%>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```

# Set directory structure

```{r}
t1 <- Sys.time()
#path to apsimx 
apsimx <- "C:/Data/ApsimxLatest/ApsimX/Bin/Models.exe"
apsimx_flag <- "/Edit"
apsimx_file <- "C:/Data/Master/01raw-data/ApsimxFiles/20200520Demo.apsimx"
apsimx_sims_temp <- "C:/Data/Master/03processed-data/apsimxFiles/temp.apsimx"
apsimx_sims_dir <- "C:/Data/Master/03processed-data/apsimxFiles/"
apsimx_config <- "C:/Data/Master/03processed-data/configSoilWat"

# Node Path - copied from ApsimX UI

initialSW <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.InitialConditions.SW = "
DUL <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.DUL = "
LL <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.LucerneSoil.LL = "
LL15 <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.LL15 = "
# PAWC <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.PAWC = "
SAT <- ".Simulations.New Zealand.AshleyDene.Factors.SowingDate.SD.ADsoils.Physical.SAT = "
# Keys
sites <- unique(SW_DUL_LL$Experiment)
SDs <- paste0("SD", 1:10)

# Vectorise the values 
for(j in sites){
  for(i in SDs){
    # Filter the right values 
    SDsw <- SW_DUL_LL[SowingDate == i & Experiment == j]$SW
    SDDUL <- SW_DUL_LL[SowingDate == i & Experiment == j]$DUL
    SDLL <- SW_DUL_LL[SowingDate == i & Experiment == j]$LL
    apsimx_sw <- paste0(initialSW,
                        paste(SDsw,collapse = ","))
    apsimx_DUL <- paste0(DUL,
                         paste(SDDUL,collapse = ","))
    apsimx_LL <- paste0(LL,
                        paste(SDLL,collapse = ","))
    apsimx_LL15 <- paste0(LL15,
                          paste(SDLL,collapse = ","))
    apsimx_SAT <- paste0(SAT,
                         paste(SDDUL,collapse = ","))
    # Open a text file
    f <- file(paste0(apsimx_config, j, i, ".txt"), "w")
    # Write values into the file 
    cat(apsimx_sw,
        apsimx_DUL,
        apsimx_LL,
        apsimx_LL15,
        apsimx_SAT,"\r",
        sep = "\r", 
        file = f, 
        append = TRUE)
    # Close the file and clean it from memory 
    close(f)
    rm(f)
    gc()
  }

}

t2 <- Sys.time()
t2 - t1
```

# Invoke Apsimx

```{r}
t1 <- Sys.time()
for(j in sites){
   for(i in SDs){
     # Edit the base apsimx file and save it to a new name
     ## modify the apsimx file 
     system(paste(apsimx, apsimx_file, apsimx_flag, paste0(apsimx_config, j, i,".txt")))
     ## rename the modified one
     system(paste("cp", apsimx_file, paste0(apsimx_sims_dir, "Modified", j, i, ".apsimx")))
     ## delete the temp apsimx 
     # system(paste("rm", paste0(apsimx_sims_dir, "temp*")))
   }
  }
t2 <- Sys.time()
t2 - t1
```

```{r}
# system(apsimx)
t1 <- Sys.time()
# system(paste(apsimx, paste0(apsimx_sims_dir,"*.apsimx"), "/NumberOfProcessors:8"))
t2 <- Sys.time()
t2 - t1
```

It only takes 6 seconds for the apsimx ui to run 10 simulations. 