---
title: "Data_tidy"
output: github_document
---

## Aim 

1. improve the variable names to the same logic
2. combin `ObsAll` with Richard data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 11, fig.height = 7, dpi = 300)
source("R/packages.R")
source("R/functions.R")
```



```{r}

```


## Exam all variable names

```{r read in data}
obsall <- read_excel("../Data/Lucerne/ObsAll.xlsx", guess_max = 15000)  %>% # enlarge number of guess format of the variable type 
  as_tibble( .name_repair = "unique") %>%  # fix the name 
  as.data.table() # change to data.table format 
col_xiumei <- colnames(read_excel("../Data/Lucerne/ObsAllData.xlsx", n_max = 1)) # similar names?

not_in_xiumei <- setdiff(colnames(obsall), col_xiumei)

obsall[, c("SimulationName...1", not_in_xiumei), with =FALSE][!is.na(SW11)]$SimulationName...1 %>% 
  unique()
```

The dataset `ObsAllData` xiumei using has no 
Nekia/Iversen_12(dry/irri)

`NekiaDefoliation`:
1. Soil moisture measurement intervals?
2. measured volumetric soil water content? 

others are mm? 


`Elliot dry/irri` have only shootbiomass?! 
`GattonDefoliation` has only biomass data - no water

`AshlydeenDefoliation`  has SWC and Height/shootbiomass 

```{r}

colnames(obsall) # the dash in colnames is a pain in the ***
obsall <- obsall[, -c("Clock.Today...8", "SimulationName...129")] # duplicated cols
setnames(obsall, colnames(obsall), c("SimulationName", "Clock.Today", colnames(obsall)[-(1:2)]))

col_essential <- colnames(obsall)[1:2] # SimulationName and Clock.Today are consistent across all 
col_swc <-  grep("sw", colnames(obsall), ignore.case = TRUE, value = TRUE)

cols <- c(col_essential, "Shootbiomass", col_swc) # only extract the biomass and swc relevant

DT_Biomass_swc <- melt(obsall[,..cols], id.vars = col_essential)[!is.na(value) & value != 0 # get rid of NAs
                                               ][, variable := gsub("-","to", variable) # get rid of dashes
                                                 ]

```

```{r LIGHT VISU}
DT_Biomass_swc[!variable %in% c("SWCerror", "Shootbiomass")]  %>% 
  ggplot(aes(Clock.Today, value, color = variable)) +
  geom_point() + 
  theme_water()

DT_Biomass_swc[variable == "SWCerror"]$SimulationName %>% unique()

dt <- DT_Biomass_swc[!variable %in% c("SWCerror") & value != 0, .(mean = mean(value, na.rm = T)), by = .(SimulationName, Clock.Today, variable)]%>% 
  dcast(., SimulationName + Clock.Today ~ ...)
colnames(dt)
col_rowsum <- colnames(dt)[-c(1:2, length(dt))]
dt[is.na(SWC)]
dt[!is.na(SW10)]

dt_profile <- dt[, SWC := ifelse(is.na(SWC), rowSums(.SD, na.rm = T), SWC), .SDcols = col_rowsum # calculate the profile water
   ][, SimulationName := ifelse(SimulationName == "AshlydeenDefoliation", "AshleyDeneDefoliation", SimulationName) # fix typo
     ][, Site := gsub("SowingDate.+|Defoliation|Water.+", "", SimulationName) # add a new variable Site
       ]
dt_profile %>% 
  ggplot(aes(Clock.Today, SWC, color = Site)) +
  geom_point() + 
  theme_water()
dt_profile[Site != "Gatton"  & SWC > 10 & SWC!=0] %>% 
  ggplot(aes(Clock.Today, SWC, color = Site, shape = Site)) +
  geom_point(size = 2.5) + 
  theme_water() + 
  scale_color_viridis_d(option = "D") +
  scale_x_datetime(date_breaks = "2 year", date_labels = "%Y", name = "") +
  theme( legend.position = c(.90, .72)) +
  scale_shape_manual(values=c(20:9)) +
  ggtitle("Soil water content in the PROFILE for all dataset")
ggsave("../imgs/SWC_in_profile_mm.png", height = 7, width = 11)
# dt_profile[Clock.Today > "2005-01-01" & Clock.Today < "2010-10-31"]

```

no need for swcerror
~summarised all layers to SWC?~ Done
`SWCerror` is from Iversen_12/Iversen_9/AshleyDene

One value from Nekia has no SWC profile value
and don't know what is the interval for the measurement to convernt % to mm


```{r bring in the richard water}
con_richard <- dbConnect(SQLite(), "../Data/Richard.sqlite3")

tabs <- con_richard %>% 
  dbListTables()

obs_richard <- dbReadTable(con_richard, "SoilWater") %>% 
  mutate(Date = lubridate::dmy(Date))
obs_richard %>% 
   ggplot(aes(Date, SWC.2.3.m..mm., color = Site, shape = Rep)) +
  geom_point() + 
  theme_water()
```


## There is no need to combine richard data set at this stage into the `ObsAll`

Biomass is a poor variable across all dataset

`Shootbiomass` is more consistent 

```{r subset only biomass and SWC}

dt_profile[,.(SimulationName, Clock.Today, Site,SWC, Shootbiomass )
           ][, (c("SWC", "Shootbiomass")):= lapply(.SD, function(x){
             x = ifelse(x == 0, NA, x)
             x
           }), .SDcols = c("SWC", "Shootbiomass") # replace all the misterous 0s with NAs
           ][, SimulationName := ifelse(SimulationName == "HudsonDefoliation", 
                                        "HudsonDefoliationCutting", 
                                        SimulationName)
               ] %>% 
  unique() %>% 
  write.xlsx("../Data/20191022_aboveground_swc.xlsx", sheetName = "Observed")

```

## run all simulation at the same time 

`Hudson` has no `SWC` obeserved values? 
becusae the simulation name does not match 
**Same as the rest of Oz and argentina data set**

## fix the simulation names 

```{r}
simNames <- dt_profile$SimulationName %>% unique() %>% grep("Defoliation$", x = . , value = TRUE)

dt_profile <- dt_profile[,.(SimulationName, Clock.Today, Site,SWC, Shootbiomass)
           ][, (c("SWC", "Shootbiomass")):= lapply(.SD, function(x){
             x = ifelse(x == 0, NA, x)
             x
           }), .SDcols = c("SWC", "Shootbiomass") # replace all the misterous 0s with NAs
           ][, SimulationName := ifelse(SimulationName %in% simNames, paste0(SimulationName, "Cutting"),
                                                    SimulationName)]
dt_profile$SimulationName %>% unique()
dt_profile %>% 
  write.xlsx("../Data/20191031_aboveground_swc.xlsx", sheetName = "Observed")
```


```{r}
dt_profile[SimulationName == "Iversen_9SowingDateSD3Waterirr"]
```

