---
title: "Chapter 5"
output:
  word_document:
    reference_docx: FRC dissertation template.docx
  html_document:
    df_print: paged
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 10, fig.height = 7, 
                      dpi = 300)
options(scipen = 999)
#Constants
outlier.colour = "#ff0000"
source(here::here("02Scripts/R/packages.R"))
source(here::here("02Scripts/R/functions.R"))
path_richard <- "C:/Users/cflfcl/Dropbox/Data/APSIM_Sim.xlsx"
id_vars <- c("Experiment", "SowingDate", "Clock.Today", "DAS")

data_sw <- read_Sims(path = path_richard)

value_vars <-  grep("SWmm\\.\\d.", colnames(data_sw), value = TRUE)
sw_mean_new <- colwise_meanSW(data_sw)

# Colour p
blues <- c("#0f5e9c",
           "#2389da",
           "#1ca3ec",
           "#5abcd8",
           "#74ccf4")
names(blues) <- blues 
ggplot(data.frame(x = blues, y = 1),aes(x, y, fill = x)) +
  geom_col() +
  scale_fill_manual(name = "", values = blues)+
  theme_void()

magicDate <- "2011-06-25"
```


# Introduction 


# Material and method 

## Workflow description 

1. slurp simulation configuration. one base apsimx and modified into 20 or one 
apsimx file has 20 simulations in it.   
2. edit apsimx file. the difficult part is to find a reliable tool to modify apsimx 
files.  
3. optimisation. DEoptim function choices, had a SSR calculation for a cost function 
when doing the optimisation with junqi. 



## APSIMX-Slurp

## APSIMX-Lucerne

## Workflow 


# Results 

## Best values 

```{r}
rdsfiles <- list.files("c:/Users/cflfcl/OneDrive - Lincoln University/transfer/",
                       full.names = TRUE)
l <- lapply(rdsfiles, readRDS)

names(l) <- basename(rdsfiles)

View(l$opt.res_AshleyDene_SD1)
l$opt.res_AshleyDene_SD1$member$bestmemit %>% View()
bestmemit <- as.data.table(l$opt.res_AshleyDene_SD1$member$bestmemit, keep.rownames = TRUE) %>% 
  melt.data.table(id.vars = "rn",variable.factor = FALSE)
storepop <- rbindlist(lapply(l$opt.res_AshleyDene_SD1$member$storepop, as.data.table, keep.rownames = TRUE), 
                      idcol = "itr") %>% 
  melt.data.table(id.vars = c("itr","rn"),variable.factor = FALSE)

parameters <- readRDS(here::here("_targets/objects/parameters"))
parnms <- parameters[,.(parameter)
                     ][, variable := paste0("par", 1:.N)]
storepop <- storepop[parnms, on = "variable"]

base_p <- bestmemit[parnms, on = "variable"
                    ][, rn := as.integer(rn)] %>% 
  ggplot(aes(rn, value))+
  geom_point(data = storepop, aes(itr, value), color = "grey80", alpha = 0.5) +
  geom_point(color = "#FF0000") +
  facet_wrap(~parameter, scales = "free_y")+
  theme_water() +
  theme(text = element_text(size = 20)) +
  labs(x = "Iteration", y = "Value range")
# ggsave(filename = "20210607ADsd1to.png",
#        base_p, dpi = 320, height = 7, width = 9)
```

```{r}
fit.par <- data.table(estimates = l$opt.res_AshleyDene_SD1$optim$nfeval, 
                      cost = l$opt.res_AshleyDene_SD1$optim$bestval)

cbind(parameters,fit.par)
```

```{r}

cost <- data.table(bestval = l$opt.res_AshleyDene_SD1$member$bestvalit , 
                   iter = 1:(l$opt.res_AshleyDene_SD1$optim$iter))

cost %>% 
  ggplot(aes(iter, bestval))+
  geom_point(color = "#FF0000") +
  # facet_wrap(~parameter, scales = "free_y")+
  theme_water() +
  theme(text = element_text(size = 20)) +
  labs(x = "Iteration", y = "Value range")
```
```{r}
dt <- read_dbtab("../../01Data/ApsimxFiles/SingleSlurp.db", "PredictedObserved")
dt[Clock.Today>=magicDate] %>% 
  ggplot(aes(Clock.Today, `Pred-Obs.SWCmm`))+
  geom_point()
dt[Clock.Today>=magicDate] %>% 
  ggplot(aes(Clock.Today, Predicted.SWCmm))+
  geom_line()+
  geom_point(aes(y = Observed.SWCmm)) 

(dt[Clock.Today>=magicDate]$`Pred-Obs.SWCmm`) ^ 2%>% 
  sum(na.rm = TRUE)

```


# Discussion
