---
title: "Data_acquisition"
author: "jian (AKA Frank) liu"
date: "06/02/2021"
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_depth: 3
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
source(here::here("02scripts/R/packages.R"))
source(here::here("02scripts/R/functions.R"))
path_richard <-  "c:/Users/cflfcl/Dropbox/Data/APSIM_Sim.xlsx"
file_richard <-  read_excel(path_richard, guess_max = 10300, sheet = 2,
                          skip = 9, .name_repair = "universal") %>% 
  as.data.table()

apsimx_obs <- "C:/Data/ApsimX/ApsimXLatest/Prototypes/Lucerne/ObsAllData.xlsx"
obsalldata <-  read_excel(apsimx_obs, guess_max = 10300) %>% 
  as.data.table()

```

# Richard and obsalldata set into sqlite?

```{r richard}
introduce(file_richard)
# plot_intro(file_richard)
# plot_missing(file_richard)
introduce(obsalldata) %>% 
  melt.data.table()

goodcols <- choose_cols(obsalldata)
badcols <- colnames(obsalldata)[!colnames(obsalldata) %in% goodcols ]
obsalldata <- obsalldata[,..goodcols]
```

There are `r length(goodcols)` good column have at least one value.\
In contrast, these variables `r badcols` have none values.

what is available already?

```{r}
obsalldata$SimulationName %>% 
  unique()
```

Ashley Dene treatment showed up. What is there?

```{r}
AD <- obsalldata[SimulationName %like% "Ashley"]
goodcols_AD <- choose_cols(AD)
length(grep("error", goodcols_AD, value = TRUE))
```

It had `r length(goodcols_AD)` cols.\
KEEP these variable or just remove all AD and add in the new ones

```{r}
# MELT the DT to a long format for fast filter
obs_long <- obsalldata %>% 
  melt.data.table(id.vars = c("SimulationName", "Clock.Today"), na.rm = TRUE) 

# Correct a typo in the simulation name col
obs_long <- obs_long[SimulationName == "AshlydeenDefoliation",
         SimulationName := "AshleyDeneDefoliation"
         ][value!=0]

# Filter out the missing values and any data from AshleyDene
# Then cast it back to wide format
obs_wide <- obs_long %>% 
  dcast.data.table(SimulationName + Clock.Today ~ variable)

# obs_wide %>%
#   write.xlsx(file = "ObsAllData.xlsx", sheetName = "ObsAllData")
# colnames(obs_wide)

```

Possible duplicated columns Biomass_Wt, ShootWt, Shootbiomass
Plantpopulation, Shootpopulation SWC, Total_SW

**Assume that all biomass unit is KG/HA** Not sure about the
`Biomass_Wt` column in `GattonDefoliation`\
So could combine the rest of the two.

```{r}
aboveground <- obs_wide[, .(SimulationName, Clock.Today, Biomass_wt, ShootWt, Shootbiomass)] %>% 
  melt.data.table(id.vars = c("SimulationName", "Clock.Today"), na.rm = TRUE)
aboveground[!is.na(value) & value != 0 ] %>% 
  ggplot(aes(Clock.Today, value) )+
  geom_point()+
  facet_grid( variable ~ .)
siteA <- unique(aboveground[variable == "Shootbiomass" & !is.na(value)]$SimulationName)
siteB <- unique(aboveground[variable == "ShootWt" & !is.na(value)]$SimulationName)

dup_cols <- siteA[siteA %in% siteB]
# aboveground[SimulationName %in% dup_cols]
```

"BalcarceDefoliationCutting" "TrenqueLauquenDefoliationCutting" have
identical values in two different colnames.

Investigate `Plantpopulation, Shootpopulation`

```{r}
aboveground <- obs_wide[, .(SimulationName, Clock.Today, PlantPopulation, ShootPopulation)] %>% 
  melt.data.table(id.vars = c("SimulationName", "Clock.Today"))
aboveground[!is.na(value) & value != 0 ] %>% 
  ggplot(aes(Clock.Today, value) )+
  geom_point()+
  facet_grid( variable ~ .)
```

investigate `SWC, Total_SW`

```{r}
aboveground <- obs_wide[, .(SimulationName, Clock.Today, SWC, Total_SW)] %>% 
  melt.data.table(id.vars = c("SimulationName", "Clock.Today"))
aboveground[!is.na(value) & value != 0 ] %>% 
  ggplot(aes(Clock.Today, value) )+
  geom_point()+
  facet_grid( variable ~ .)
aboveground[variable=="Total_SW" & value > 750]
```

1.  Combine `ShootWt` with `Shootbiomass`\
    \~Seems `ShootWt` contains `Shootbiomass` for all listed sites.\~
    **Remove Shootbiomass and its sme**

2.  `Plantpopulation, Shootpopulation` are different. remain intact

3.  `Total_SW` is from `JimbourSowingDate*`. pretty high, left
    untouched.

## Existing variable names can be reused

"ET", "Height", "Heighterror", "LAI", "LeafWt", "RootWt", "SLA", "SWC",
"ShootPopulation", "ShootWt"

Not sure about the unit of "SLA"

```{r checking existing SLA}
hist(obs_wide$SLA)
```

Seems in the $cm^2/g$

## Aggregate Richard's data into the obsalldata excel

```{r}
colnames(file_richard)

```

Quite a lot columns.

| Biomass          | Root                                         | SW     | Phenology    |
|------------------|----------------------------------------------|--------|--------------|
| Height (cm)      | Root.Total (kg/ha) = Crown + 0-5cm + 5-30cm) | SWC.\* | MS.node.No   |
| Shoot.m2         | Crown? (kg/ha)                               |        | Growth.Stage |
| Leaf.DM (kg/ha)  | Plant.No....48 (m\^2)                        |        |              |
| Stem.DM (kg/ha)  |                                              |        |              |
| Total.DM (kg/ha) |                                              |        |              |
| SLA FM (cm2/g)   |                                              |        |              |
| LAImod           |                                              |        |              |
| SLA DM (cm2/g)   |                                              |        |              |

```{r}
idvars <- c("Data","Site", "Date", "Season", "Sowing.Date", 
            # "Rep", "Plot",  
            "Seed", "Rotation.No.", "Harvest.No.",  "DAS")
valvars <- c("Height", "Shoots.m2", "Total.DM", "Leaf.DM", "Stem.DM","SLA..FW.",
             "SLA..DW.", "LAImod", "Root.Total", "Crown", 
             paste0("SWC.0.", 1:23), "SWC.2.3.m..mm.",
             "MS.node.No", "Growth.stage")
# file_richard

cols <- c(idvars, valvars)
richard_long <- file_richard[Data %in% c("Biomass", "Root",
                                         "Phenology", "Soil water") &
               Seed == "CS",
             ..cols
             ][, SWC.0.1:= SWC.0.1+SWC.0.2
               ][, SWC.0.2 := NULL] %>% 
  setnames(., paste0("SWC.0.", c(1,3:23)), paste0("SWmm(", 1:22,")")) %>% 
  melt.data.table(id.vars = idvars, na.rm = TRUE)

```

```{r}
No.ofObs <- richard_long[, .N, by = c(idvars, "variable")]
hist(No.ofObs$N)
No.ofObs[N < 3]$Data %>% 
  unique()
hist(file_richard$Total.DM)
```

There are some harvest or assessment had only 1 observation or no
replication.

```{r}
groupkey <- c(idvars, "variable")
agg <- richard_long[, unlist(lapply(.SD, function(x) 
  list(mean=mean(x, na.rm = TRUE),
       sd = sd(x, na.rm = TRUE),
       n = .N,
       Upper = max(x, na.rm = TRUE),
       Lower = min(x, na.rm = TRUE))
  ), recursive = FALSE), by = groupkey]

```

Change the aggregated DT to wide format as APSIM requires.

```{r}
keycols <- c(idvars, "variable", "value.mean")

mean_se <- agg[, se := value.sd/sqrt(value.n)
               ][!(Data == "Phenology" & variable == "LAImod")]
obs_Richard <- mean_se[,..keycols] %>% 
  dcast.data.table(Data + Site + Sowing.Date + Season + Date + 
                     DAS + Rotation.No.+ Harvest.No.~ variable,
                   value.var = c("value.mean"))
```

Necessary to tidy up the names

```{r}
# Connect to the simulation output db 
# And grep colnames 
# path_db <- here::here("01Data/ApsimxFiles/LucerneValidation.db")
# conn <- dbConnect(SQLite(), path_db)
# 
# report <- dbReadTable(conn, "Report", check.names = FALSE )
# colnames(report)

# Rename obs_wide to match the colnames 
 # colnames(obs_Richard)

setnames(obs_Richard, 
         c("Sowing.Date", "Date","Shoots.m2", "Total.DM", "Leaf.DM","Stem.DM",
           "LAImod", 
           "Root.Total", "SWC.2.3.m..mm.",
           "Growth.stage"),
         c("SowingDate", "Clock.Today","ShootPopulation", "ShootWt", "LeafWt",
           "StemWt", "LAI", "RootWt", "SWCmm", "GrowthStage"))
obs_Richard[, SimulationName := paste0(Site, "SowingDate", SowingDate)
            ][, (c("Site", "SowingDate","Data","Season","DAS",
                   "Rotation.No.","Harvest.No.")) := NULL]
# colnames(obs_wide)

obs_wide <- rbindlist(list(obs_wide, obs_Richard), use.names = TRUE, fill = TRUE)

```

[FAKE ZEROS NEED TO BE REPALCED BY
NAs](https://github.com/frank0434/Master/issues/29#issuecomment-774422595)

```{r}
# colnames(obs_wide)

SDCOLS <- colnames(obs_wide)[-(1:2)]
obs_wide[, (SDCOLS) := lapply(.SD, function(x) ifelse(x == 0, NA, x)), 
         .SDcols = SDCOLS]
```

## Output the big obsalldata

```{r}
write.xlsx(x = obs_Richard[, Clock.Today := as.Date(Clock.Today)], 
           file = here::here("01Data/ApsimxFiles/ObsAllData.xlsx"), 
             sheetName = "ObsAllData")

```
