---
title: "1. Debug targets"
output: 
  html_document:
    toc: true
    toc_depth: 2 
    code_folding: hide
---

```{r setup, include=FALSE}
source(here::here("02Scripts/R/packages.R"))
source(here::here("02Scripts/R/functions.R"))
path_richard <- "C:/Users/cflfcl/Dropbox/Data/APSIM_Sim.xlsx"
id_vars <- c("Experiment", "SowingDate", "Clock.Today", "DAS")

data_sw <- read_Sims(path = path_richard)

value_vars <-  grep("SWmm\\.\\d.", colnames(data_sw), value = TRUE)
sw_mean_new <- colwise_meanSW(data_sw)

```


# Inspect ranges

```{r fig.height=10}
DUL_LL_range <- doDUL_LL_range(SW = sw_mean_new,
                               startd = "2011-06-25")
# CF 0.95
DUL_LL_range[, ':=' (i.SW.DUL = i.SW.DUL * 0.95,
                     i.SW.LL = i.SW.LL * 0.95)]
DUL_LL_range

SW_mean_new

data_SW
range_check <- function(DT,  layer, boundry = c("DUL","LL")){
  yval <-  paste0("SWmm.",layer, "..mean")
  cols <- c("Experiment", "Clock.Today", "SowingDate",yval)
  DT <- DT[,..cols]
  # yval <- paste0("`",layer,"`")
  P <- DT[,..cols] %>% 
    ggplot(aes_string("Clock.Today", yval)) + 
    geom_point() +
    facet_grid(SowingDate  ~ Experiment) 
  if(boundry =="LL"){
    dt_sub <- DT[order(SWmm.1..mean), .SD[1], by = .(Experiment, SowingDate)]
    P <- P + 
      geom_point(data = dt_sub , aes_string("Clock.Today", yval),  color ="red", size = 5)
  } else if (boundry == "DUL"){
    dt_sub <- DT[order(SWmm.1..mean, decreasing = TRUE), .SD[1], by = .(Experiment, SowingDate)]
    P <- P + 
      geom_point(data =dt_sub, aes_string("Clock.Today", yval),  color ="red", size = 5)
  } else{
    print("Don't know what to draw. DUL or LL")
  }
  return(P)
  
}
range_check(SW_mean_new, 1, boundry = "DUL")
range_check(SW_mean_new, 1, boundry = "LL")

SW_mean_new[Experiment =="AshleyDene" & SowingDate == "SD9"]$Clock.Today %>% range()
  ggplot(aes(Clock.Today, SWmm.1..mean)) +
  geom_point()

```
It is not ideal to have a DUL from the end of the experiments. 
need to constrain the period 
**action** - modify the DUL and LL finder to lock the period. 

LL seems not the lowest since we constrian the period. 
maybe the end of June is good?
```{r fig.height=10}


range_check(SW_mean_new, 1, boundry = "LL")
```

```{r, fig.height=14, fig.width=9}
sdcols <- grep("sd", colnames(SW_mean_new), value = TRUE)
neededcols <- c(id_vars, sdcols)
DT_sd <- SW_mean_new[,..neededcols
                 ][, SWmm.1..sd := SWmm.1..sd /200
                   ][, (paste0("SWmm.", 2:22,"..sd")) := lapply(.SD, function(x) x/100),
                     .SDcols = paste0("SWmm.", 2:22,"..sd"),
                     by = id_vars]

tar_load(DUL_LL_range)


DUL_sd <- DT_sd %>% 
  melt.data.table(id.vars = id_vars, value.name = "SW.sd.DUL",
                  variable.name = "Depth",
                  variable.factor = FALSE)
DUL_sd[, Depth := as.integer(gsub("\\D", "", Depth))]
LL_sd <- DT_sd %>% 
  melt.data.table(id.vars = id_vars, value.name = "SW.sd.LL",
                  variable.name = "Depth",
                  variable.factor = FALSE)
LL_sd[, Depth := as.integer(gsub("\\D", "", Depth))]

DUL_LL_range <- DUL_sd[DUL_LL_range, on = c("Experiment", "SowingDate", "Depth"," Clock.Today == Clock.Today.DUL")] 
DUL_LL_range <- LL_sd[DUL_LL_range, on = c("Experiment", "SowingDate", "Depth"," Clock.Today == Clock.Today.LL")] 


DUL_LL_range[SowingDate %in% paste0("SD", 1:5)]%>% 
  ggplot(aes(x = Depth))+
  geom_point(aes(y = SW.DUL))+
  geom_line(aes(y = SW.DUL)) +
   geom_line(aes(y = SW.LL))+
  # geom_point()+
  scale_x_reverse() +
  coord_flip() +
  geom_point(aes(y = SW.LL)) +
  geom_errorbar(aes(ymin = SW.DUL - SW.sd.DUL, ymax = SW.DUL + SW.sd.DUL))+
  # geom_point(aes(y = Low.DUL), color = "red") +
  # geom_point(aes(y = High.DUL), color = "blue") +
  geom_errorbar(aes(ymin = SW.LL - SW.sd.LL, ymax = SW.LL + SW.sd.LL))+
  # geom_point(aes(y = Low.LL), color = "red") +
  # geom_point(aes(y = High.LL), color = "blue") +
  facet_grid(  SowingDate ~ Experiment) +
  theme_water() 
ggsave("Data/images/DUL_LL.png", width = 9, height = 12, dpi = 320)
```
# check met files and cumTT
```{r}
tar_load(starts_with("met"))
met_AshleyDene
met_Iversen12
tar_load("cumTT")
cumTT %>% 
  ggplot(aes(Clock.Today, AccumTT)) +
  geom_point() +
  facet_grid( Experiment ~ . ) +
  theme_water()

```
# Check observed LAI and SW
```{r}
tar_read(observed)

```
# Check template
```{r}
tar_read(template)
```
# Check CoverData
```{r}
tar_load(CoverData)
CoverData[ SowingDate == "SD2"] %>% 
   ggplot(aes(Clock.Today, AccumTT)) +
  geom_point() +
  facet_grid( Experiment ~ . ) +
  theme_water()
CoverData[ SowingDate == "SD2" & Experiment == "AshleyDene"] %>% 
   ggplot(aes(Clock.Today, LAI)) +
  geom_point() +
  geom_line() +
  facet_grid( Experiment ~ . ) +
  theme_water()

# BRING IN THE RAW VALUES 
sd2LAI <- read_excel("C:/Data/Master/Data/ProcessedData/CoverData/ObservedAshleyDeneSD2.xlsx")
sd2LAI %>% 
  ggplot(aes(Clock.Today, LAImod)) +
  geom_point() +
  geom_line() +
  facet_grid( Experiment ~ . ) +
  theme_water() +
  ggtitle("AshleyDene SD2")

```
## Debug for LAI interpolatation 

```{r}
tar_load(LAI_Height)
tar_load(sowingDates)
tar_load(cumTT)
LAI_Height
sowingDates
cumTT
interp_LAI(biomass = LAI_Height, sowingDates, cumTT)[]
# observation <- LAI_Height[Experiment == "AshleyDene" & SowingDate == "SD2"]


LAI_Height_SD <- merge.data.table(LAI_Height, sowingDates,
                                  by = c("Experiment", "Clock.Today" , "SowingDate"), 
                                    all= TRUE)[,':='(LAImod = ifelse(is.na(LAImod), 0, LAImod),
                                                     Height = ifelse(is.nan(Height), NA, Height))]
  
  LAI_wide <- dcast.data.table(LAI_Height_SD, 
                               Experiment + Clock.Today ~ SowingDate, 
                               value.var = "LAImod" )

  
  
  DT <- merge.data.table(cumTT, LAI_wide, by = c("Experiment", "Clock.Today"), 
                         all.x = TRUE)
  # DT[, SD2:= zoo::na.approx(SD2, na.rm =FALSE)]
  
  
  DT <- melt.data.table(data = DT, 
                        id.vars = c("Experiment", "Clock.Today", "AccumTT"), 
                        value.name = "LAI",
                        variable.name = "SowingDate", variable.factor = FALSE)
  
  DT <- DT[, LAI:= zoo::na.approx(LAI,  na.rm = FALSE) , by = .(Experiment, SowingDate) ]
  
  DT <- DT[, LAI:= zoo::na.approx(LAI, na.rm = FALSE) ]
  DT %>% 
    ggplot(aes(Clock.Today, LAI)) +
  geom_point() +
  geom_line() +
  facet_grid( Experiment ~ . ) +
  theme_water() +
  ggtitle("AshleyDene SD2")
  DT <- DT[, ':='(k = 0.94)
     ][Experiment == "AshleyDene" & Clock.Today %between% c( '2011-11-30','2012-03-01'),
       k:= 0.66][, LI := 1 - exp(-k * LAI) ]
  

```
# Check SW_INITIALS
```{r}
tar_load(SW_initials)
SW_initials[]
cbp1 <- c("#FF0000", "#00FF00", "#0000FF", "#fab80a","#8c06ff", 
          "#dceeff", "#c6deff", "#a7ccff", "#85a8e3","#6c9bd0")
p_initialSW <- SW_initials %>% 
   ggplot(aes(x = Depth, color = SowingDate))+
  geom_point(aes(y = SW))+
  geom_line(aes(y = SW)) +
  scale_x_reverse() +
  coord_flip() +
  facet_grid(  ~ Experiment ) +
  theme_water() +
  scale_color_manual(values = cbp1)
SW_initials


errorbar <- dcast.data.table(SW_initials[SowingDate%in%paste0("SD",1:5)],Experiment + SowingDate + Clock.Today + Depth ~ Stats, value.var = "SW")
errorbar[Depth == 1, se := sd/200/2
         ][Depth != 1, se:= sd/100/2]
p_initialSW <- p_initialSW + 
  geom_errorbar(data = errorbar,
                aes(ymin = mean - se, ymax = mean + se), color = "grey")
p_initialSW
ggsave("Data/images/initialSW.png",plot = p_initialSW, width = 7, height =6, dpi = 320)

```

# Check DUL AND LL 

```{r}
tar_load(DUL_LL_range_arbitrary)
tar_load(esti_DUL_LL)
DUL_shift <- esti_DUL_LL %>% 
  ggplot(aes(Depth)) +
  geom_point(aes(y = DUL, color = "DUL")) + 
  geom_smooth(aes(y = DUL, color = "DUL"), se = FALSE,) +
  geom_point(aes(y = SW.DUL, color = "POSTDUL")) + 
  geom_smooth(aes(y = SW.DUL, color = "POSTDUL"), se = FALSE) +
   geom_point(aes(y = DUL * 0.95, color = "arbitraryDUL")) + 
  geom_smooth(aes(y = DUL * 0.95, color = "arbitraryDUL"), se = FALSE) +
  coord_flip()+
  facet_wrap(Experiment ~ .)+
  scale_x_reverse(limits = c(23, 0), expand = c(0,0)) 
  
DUL_shift +
  theme_water()+
  scale_color_manual(values = c("DUL" = "#FF0000", "POSTDUL" = "#0000FF", 
                                "arbitraryDUL" = "#00FF00"))
```


.Simulations.Slurp
.Simulations.SlurpMorris

# Check BDs

```{r}
tar_load(BDs)
p_BD <- BDs %>% 
  ggplot(aes(x = Depth))+
  geom_point(aes(y = Low))+
  geom_line(aes(y = Low)) +
  geom_line(aes(y = High))+
  geom_point(aes(y = High)) +
  scale_x_reverse() +
  coord_flip() +
  facet_grid(  ~ Experiment , scales = "free_x") +
  theme_water()
ggsave("Data/images/p_BD.png",plot = p_BD, width = 7, height =6, dpi = 320)

```

# Check LAI_input 

```{r}
tar_load(LAI_input)
LAI_input[1:5]
tar_load(observed)
observed
```

# Check relativeSW
```{r}
tar_load(relativeSW)

relativeSW %>% 
  ggplot(aes(Clock.Today, relativeSW, color = SowingDate)) +
  geom_point() +
  geom_line()+
  scale_x_date(date_breaks = "8 weeks") +
  geom_smooth() + 
  facet_grid( Experiment ~.)

```


# Check winter_AD/I12
```{r}
tar_load(winter_AD)
tar_load(winter_I12)
winter_AD
winter_I12
tar_load(list_AD)
tar_read(list_I12)
list_AD$data[[1]]
```

# check DUL estimation 
```{r}
tar_load(esti_DUL_AD)

esti_DUL_AD$results[[1]]
esti_DUL_AD$esti[[1]]
esti_DUL_AD$data[[1]]
esti_DUL_AD[1,]
tar_load(DUL_LL_range)
DUL_LL_range

esti_DUL_AD[, unlist(results, recursive = FALSE), by = .(Experiment, SowingDate, Depth)]


rbindlist(esti_DUL_AD$results)
tar_load(esti_DUL_LL)
esti_DUL_LL
```



# Check parameter ranges 

```{r}
tar_load(params_ranges)
names(params_ranges)[1:2]
```

# Check morris model & sampled values 

```{r}

tar_read(MorrisModels_0008acad)
tar_load(MorrisModels_0008acad)

MorrisModels_0008acad$meta

tar_load(sampledvalues)
nrow(sampledvalues)
lapply(sampledvalues, function(x){length(unique(x))})

```

